---
title: "silentinvasion2022"
author: "Darmawan Wicaksono"
date: "2022-12-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Silent invasion tweet

```{r}
# Read csv file
silentinvasionv3 <- read.csv("silentinvasiontest.csv")
```

## BOF - This part for annotation
```{r}
# /scripts/silentinvasion_annotation.R
# Purpose: Create a multi-label annotation Excel file from 'silentinvasionv3' without duplicates and without timestamp

# Load required library
library(writexl)

# Step 1: Remove duplicate tweets based on 'text' column
df_unique <- silentinvasionv3[!duplicated(silentinvasionv3$text), ]

# Step 2: Drop 'created_at' column if it exists
if ("created_at" %in% colnames(df_unique)) {
  df_unique$created_at <- NULL
}

# Step 3: Keep only the first 100 rows
df_sample <- head(df_unique, 100)

# Step 4: Define emotion categories
emotion_labels <- c("anger", "disgust", "fear", "happy", "sadness", "surprise")

# Step 5: Create empty binary emotion columns (to be annotated later)
for (emotion in emotion_labels) {
  df_sample[[emotion]] <- 0
}

# Step 6: Save the result to Excel
write_xlsx(df_sample, path = "annotation_participant_multilabel.xlsx")
```

```{r}
# Load the necessary library
library(tidyverse)

# Read the dataset
df_count_v14 <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Exclude 'Ambigious' category and calculate the count for each remaining category
emotion_counts_v14 <- df_count_v14 %>%
  group_by(emotion) %>%
  summarise(Count = n())

# Print the counts
print(emotion_counts_v14)
```

```{r}
# /scripts/match_annotation_with_original.R
# Purpose: From df_count_v14, extract rows that match df_sample by row index and keep only 'text' and 'emotion'

# Load required library
library(writexl)

# Step 1: Ensure 'df_sample' contains the subset of interest (assumed to be already created)
#         Extract its row numbers (i.e., original row indices from df_count_v14)
matched_indices <- as.numeric(rownames(df_sample))

# Step 2: Subset df_count_v14 using those indices
df_matched <- df_count_v14[matched_indices, c("text", "emotion")]

# Step 3: Save the matched subset to Excel
write_xlsx(df_matched, path = "annotation_participant_original.xlsx")
```
## EOF - This part for annotation


```{r}
# Load the utils package
library(utils)

# Convert the date column to the ISO 8601 format
silentinvasionv3$date <- strptime(silentinvasionv3$created_at, format = "%Y-%m-%dT%H:%M:%S.%OSZ")
```


```{r}
# Extract the year from each date
library(lubridate)
silentinvasionv3$year <- year(silentinvasionv3$date)
```


```{r}
library(dplyr)
silentinvasionv3_2021_2022 <- silentinvasionv3
```


```{r}
library(stringr)

# Take out retweet header
silentinvasionv3_2021_2022$text <- str_replace(silentinvasionv3_2021_2022$text, "RT @\\w+:", "(retweetlemek)")
silentinvasionv3_2021_2022$text <- str_replace(silentinvasionv3_2021_2022$text, "RT @\\p{Lu}\\w+:", "(retweetlemek)")
silentinvasionv3_2021_2022$text <- str_replace(silentinvasionv3_2021_2022$text,"RT :","(retweetlemek)")
silentinvasionv3_2021_2022$text <- str_replace(silentinvasionv3_2021_2022$text,"rt :","(retweetlemek)")
```


```{r}
library(stringr)

# Convert hashtags into readable words
silentinvasionv3_2021_2022$text <- str_replace_all(silentinvasionv3_2021_2022$text,"#(\\w+)", "(\\1)")

```


```{r}
library(qdapRegex)

# Convert URL into readable words
silentinvasionv3_2021_2022$text <- str_replace_all(silentinvasionv3_2021_2022$text,"\\w+://\\S+", "(bağlantı adresi)")

# Replace fragments with 'http' prefix with a placeholder
silentinvasionv3_2021_2022$text <- str_replace_all(silentinvasionv3_2021_2022$text, "http\\S*", "(bağlantı adresi)")
```


```{r}
library(stringr)

# Convert references to other screennames into readable words
silentinvasionv3_2021_2022$text <- str_replace_all(silentinvasionv3_2021_2022$text,"@[a-z,_,A-Z,0-9]*", "(kullanıcı)")

```


```{r}
library(stringr)

# Get rid of unwanted characters
silentinvasionv3_2021_2022$text <- str_replace_all(silentinvasionv3_2021_2022$text, "[/\\\\+#]", "")

```


```{r}
library(tm)

# Make lower case
silentinvasionv3_2021_2022$text <- tolower(silentinvasionv3_2021_2022$text)
```


```{r}
# Delete empty parts in dataframe

# Delete NA
silentinvasionv3_2021_2022$text <- gsub("NA", "", silentinvasionv3_2021_2022$text)

# Remove whitespace
silentinvasionv3_2021_2022$text <- stripWhitespace(silentinvasionv3_2021_2022$text)

# Delete the leading and trailing spaces
silentinvasionv3_2021_2022$text <- trimws(silentinvasionv3_2021_2022$text)
```


```{r}
# Replace emojis to Turkish text translation
# DO NOT USE THIS in R, ALREADY DONE IN GOOGLE COLLABS for better computing power
# Using advance loop
library(dplyr)
library(stringr)

# Load emoticons data
emoticons_df <- read.csv("emojis_emoticons_Turkish.csv", stringsAsFactors = FALSE)

# Function to replace emojis with their Turkish translations
replace_emoticons_optimized <- function(text, mapping) {
  # Escape regex special characters in emojis
  escaped_emojis <- sapply(mapping$Emoji, regex_escape, USE.NAMES = FALSE)
  
  # Create a regex pattern that matches any of the emojis
  pattern <- paste0(escaped_emojis, collapse = "|")
  
  # Create a named vector for replacements where names are emojis and values are translations formatted with parentheses
  replacements <- setNames(paste0("(", mapping$Translated, ")"), mapping$Emoji)
  
  # Create a named vector for replacements where names are emojis and values are translations
  #replacements <- setNames(mapping$Translated, mapping$Emoji)
  
  # Use str_replace_all with the vectorized replacement approach
  text <- str_replace_all(text, pattern, function(x) replacements[x])
  return(text)
}

# Helper function to escape regex special characters in strings
regex_escape <- function(x) {
  str_replace_all(x, "([\\\\\\^\\$\\.\\|\\?\\*\\+\\(\\)\\[\\]\\{\\}\\,])", "\\\\\\1")
}

# Apply the replacement function to the text column
silentinvasionv3_2021_2022$text <- sapply(silentinvasionv3_2021_2022$text, replace_emoticons_optimized, mapping = emoticons_df)

# Cleanup whitespace
silentinvasionv3_2021_2022$text <- str_squish(silentinvasionv3_2021_2022$text)

# Delete the leading and trailing spaces (if any remain)
silentinvasionv3_2021_2022$text <- trimws(silentinvasionv3_2021_2022$text)

# DO NOT USE THIS in R, ALREADY DONE IN GOOGLE COLLABS for better computing power
```


```{r}
write.csv(silentinvasionv3_2021_2022, "silentinvasionv4_2021_2022.csv", row.names = FALSE)
```


```{r}
silentinvasionv4_2021_2022 <- read.csv("silentinvasionv4_2021_2022.csv")
```


```{r}
library(dplyr)

# Select only the "text" column and put it into a new data frame
silentinvasionv4_2021_2022cleanv4 <- select(silentinvasionv4_2021_2022, text)

# write on csv file
write.csv(silentinvasionv4_2021_2022cleanv4, "silentinvasionv4_2021_2022cleanv4.csv", row.names = FALSE)
```

```{r}
silentinvasionv4_2021_2022cleanv4 <- read.csv("silentinvasionv4_2021_2022cleanv4.csv")
```




## Hasil BERT menggunakan Google Colab
```{r}
predictedresults <- read.csv("predicted_results.csv")
```


## Silent invasion analyze using PyTorch
```{r}
# Read csv file
silentinvasionv3_predicted <- read.csv("silentinvasionv3_2021_2022cleanv3_with_emotions_v1.csv")
```

```{r}
# Potong sithik
# Taking first 51 rows from the dataset
potonganakbar <- silentinvasionv3_predicted[1:51, ]

# Save the new dataset as CSV file
write.csv(potonganakbar, "potonganakbar.csv", row.names = FALSE)
```


```{r}
# EXPERIMENT 1
# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv3_2021_2022cleanv3_with_emotions_v1.csv')

# Exclude 'Ambigious' category from the dataset
df_filtered <- df_predicted %>% 
  filter(emotion != "Ambigious")

# Plot the bar chart with the filtered dataset
df_filtered %>%
  ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
  geom_bar() +  # Create a bar chart
  theme_minimal() +  # Use a minimal theme for aesthetics
  labs(title = "Count of Emotions in Dataset (Excluding 'Ambigious')",
       x = "Emotion Category",
       y = "Frequency") +  # Add chart labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability

```


```{r}
# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv3_2021_2022cleanv3_with_emotions_v1.csv')

# Exclude 'Ambigious' category and calculate the count for each remaining category
emotion_counts <- df_count %>%
  filter(emotion != "Ambigious") %>%
  group_by(emotion) %>%
  summarise(Count = n())

# Print the counts
print(emotion_counts)

```


```{r}
# Load the necessary library
library(tidyverse)

# Read the dataset
df_ambigu <- read.csv('silentinvasionv3_2021_2022cleanv3_with_emotions_v1.csv')

# Count the number of 'Ambigious' entries
ambigious_count <- df_ambigu %>%
  filter(emotion == "Ambigious") %>%
  summarise(Count = n())

# Print the count of 'Ambigious'
print(ambigious_count)

```


```{r}
# EXPERIMENT 2
# USING TREMO Calibration
# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted2 <- read.csv('silentinvasionv3_2021_2022cleanv3_with_emotions_v2.csv')

# Plot the bar chart with the filtered dataset
df_predicted2 %>%
  ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
  geom_bar() +  # Create a bar chart
  theme_minimal() +  # Use a minimal theme for aesthetics
  labs(title = "Count of Emotions in Dataset",
       x = "Emotion Category",
       y = "Frequency") +  # Add chart labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability

```


```{r}
# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv3_2021_2022cleanv3_with_emotions_v2.csv')

# Exclude 'Ambigious' category and calculate the count for each remaining category
emotion_counts <- df_count %>%
  group_by(emotion) %>%
  summarise(Count = n())

# Print the counts
print(emotion_counts)

```



```{r}
# EXPERIMENT 3
# USING TREMO Calibration
# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v5.csv')

# Plot the bar chart with the filtered dataset
df_predicted %>%
  ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
  geom_bar() +  # Create a bar chart
  theme_minimal() +  # Use a minimal theme for aesthetics
  labs(title = "Count of Emotions in Dataset",
       x = "Emotion Category",
       y = "Frequency") +  # Add chart labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability

```


```{r}
# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v5.csv')

# Exclude 'Ambigious' category and calculate the count for each remaining category
emotion_counts <- df_count %>%
  group_by(emotion) %>%
  summarise(Count = n())

# Print the counts
print(emotion_counts)

```


```{r}
# Load the libraries
library(ggplot2)
library(dplyr)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Ensure 'emotion' is a factor
df_predicted$emotion <- as.factor(df_predicted$emotion)

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Creating the scatter plot with custom colors
ggplot(df_predicted, aes(x = date, y = emotion, color = emotion)) +
  geom_point(position = position_jitter(width = 0, height = 0.1), alpha = 0.5) +
  scale_color_manual(values = colors) +  # Apply the custom colors
  theme_minimal() +
  labs(title = "Scatter Plot of Emotions Over Time",
       x = "Date",
       y = "Emotion") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for better visibility
```


```{r}
# Load the libraries
library(ggplot2)
library(dplyr)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Ensure 'emotion' is a factor
df_predicted$emotion <- as.factor(df_predicted$emotion)

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Filter data to only include dates from June 1, 2021 to December 31, 2021
df_predicted_filtered <- df_predicted %>%
  filter(date >= as.Date("2021-06-01") & date <= as.Date("2021-12-31"))

# Manually setting the breaks to include only months from June 2021 to December 2021
monthly_breaks <- seq(from = as.Date("2021-06-01"), to = as.Date("2021-12-31"), by = "month")

# Creating the scatter plot with custom colors
ggplot(df_predicted_filtered, aes(x = date, y = emotion, color = emotion)) +
  geom_point(position = position_jitter(width = 0, height = 0.1), alpha = 0.5) +
  scale_color_manual(values = colors) +  # Apply the custom colors
  scale_x_date(limits = as.Date(c("2021-06-01", "2021-12-31")), breaks = monthly_breaks, date_labels = "%b %Y") +
  theme_minimal() +
  labs(title = "Scatter Plot of Emotions Over Time (June-Dec 2021)",
       x = "Date",
       y = "Emotion") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for better visibility
```


```{r}
# Load the libraries
library(ggplot2)
library(dplyr)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Ensure 'emotion' is a factor
df_predicted$emotion <- as.factor(df_predicted$emotion)

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Filter data to only include dates up to December 31, 2022
df_predicted_filtered <- df_predicted %>%
  filter(date >= as.Date("2022-01-01") & date <= as.Date("2022-12-31"))

# Manually setting the breaks to include only months in 2022
monthly_breaks <- seq(from = as.Date("2022-01-01"), to = as.Date("2022-12-31"), by = "month")

# Creating the scatter plot with custom colors
ggplot(df_predicted_filtered, aes(x = date, y = emotion, color = emotion)) +
  geom_point(position = position_jitter(width = 0, height = 0.1), alpha = 0.5) +
  scale_color_manual(values = colors) +  # Apply the custom colors
  scale_x_date(limits = as.Date(c("2022-01-01", "2022-12-31")), breaks = monthly_breaks, date_labels = "%b %Y") +
  theme_minimal() +
  labs(title = "Scatter Plot of Emotions Over Time (2022)",
       x = "Date",
       y = "Emotion") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for better visibility
```



```{r}
# EXPERIMENT 4
# INI SAMA DENGAN PERCOBAAN 5, NAMUN THRESHOLD NYA STANDAR 0.5
# USING TREMO Calibration
# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v6.csv')

# Plot the bar chart with the filtered dataset
df_predicted %>%
  ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
  geom_bar() +  # Create a bar chart
  theme_minimal() +  # Use a minimal theme for aesthetics
  labs(title = "Count of Emotions in Dataset",
       x = "Emotion Category",
       y = "Frequency") +  # Add chart labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability

```

```{r}
# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v6.csv')

# Exclude 'Ambigious' category and calculate the count for each remaining category
emotion_counts <- df_count %>%
  group_by(emotion) %>%
  summarise(Count = n())

# Print the counts
print(emotion_counts)

```

```{r}
# Load the libraries
library(ggplot2)
library(dplyr)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Ensure 'emotion' is a factor
df_predicted$emotion <- as.factor(df_predicted$emotion)

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Creating the scatter plot with custom colors
ggplot(df_predicted, aes(x = date, y = emotion, color = emotion)) +
  geom_point(position = position_jitter(width = 0, height = 0.1), alpha = 0.5) +
  scale_color_manual(values = colors) +  # Apply the custom colors
  theme_minimal() +
  labs(title = "Scatter Plot of Emotions Over Time",
       x = "Date",
       y = "Emotion") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for better visibility
```

```{r}
# Load the libraries
library(ggplot2)
library(dplyr)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Ensure 'emotion' is a factor
df_predicted$emotion <- as.factor(df_predicted$emotion)

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Filter data to only include dates from June 1, 2021 to December 31, 2021
df_predicted_filtered <- df_predicted %>%
  filter(date >= as.Date("2021-06-01") & date <= as.Date("2021-12-31"))

# Manually setting the breaks to include only months from June 2021 to December 2021
monthly_breaks <- seq(from = as.Date("2021-06-01"), to = as.Date("2021-12-31"), by = "month")

# Creating the scatter plot with custom colors
ggplot(df_predicted_filtered, aes(x = date, y = emotion, color = emotion)) +
  geom_point(position = position_jitter(width = 0, height = 0.1), alpha = 0.5) +
  scale_color_manual(values = colors) +  # Apply the custom colors
  scale_x_date(limits = as.Date(c("2021-06-01", "2021-12-31")), breaks = monthly_breaks, date_labels = "%b %Y") +
  theme_minimal() +
  labs(title = "Scatter Plot of Emotions Over Time (June-Dec 2021)",
       x = "Date",
       y = "Emotion") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for better visibility
```

```{r}
# Load the libraries
library(ggplot2)
library(dplyr)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Ensure 'emotion' is a factor
df_predicted$emotion <- as.factor(df_predicted$emotion)

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Filter data to only include dates up to December 31, 2022
df_predicted_filtered <- df_predicted %>%
  filter(date >= as.Date("2022-01-01") & date <= as.Date("2022-12-31"))

# Manually setting the breaks to include only months in 2022
monthly_breaks <- seq(from = as.Date("2022-01-01"), to = as.Date("2022-12-31"), by = "month")

# Creating the scatter plot with custom colors
ggplot(df_predicted_filtered, aes(x = date, y = emotion, color = emotion)) +
  geom_point(position = position_jitter(width = 0, height = 0.1), alpha = 0.5) +
  scale_color_manual(values = colors) +  # Apply the custom colors
  scale_x_date(limits = as.Date(c("2022-01-01", "2022-12-31")), breaks = monthly_breaks, date_labels = "%b %Y") +
  theme_minimal() +
  labs(title = "Scatter Plot of Emotions Over Time (2022)",
       x = "Date",
       y = "Emotion") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for better visibility
```


```{r}
# INI SAMA DENGAN PERCOBAAN 4, NAMUN THRESHOLD NYA DINAIKIN MENJADI 0.6
# EXPERIMENT 5
# USING TREMO Calibration
# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v7.csv')

# Plot the bar chart with the filtered dataset
df_predicted %>%
  ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
  geom_bar() +  # Create a bar chart
  theme_minimal() +  # Use a minimal theme for aesthetics
  labs(title = "Count of Emotions in Dataset",
       x = "Emotion Category",
       y = "Frequency") +  # Add chart labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability

```

```{r}
# INI SAMA DENGAN PERCOBAAN 5, THRESHOLD NYA SAMA DINAIKIN MENJADI 0.6, HANYA MENGULANG EKSPERIMEN 5 SAJA UNTUK VALIDASI
# EXPERIMENT 6
# USING TREMO Calibration
# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v8.csv')

# Plot the bar chart with the filtered dataset
df_predicted %>%
  ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
  geom_bar() +  # Create a bar chart
  theme_minimal() +  # Use a minimal theme for aesthetics
  labs(title = "Count of Emotions in Dataset",
       x = "Emotion Category",
       y = "Frequency") +  # Add chart labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability

```

```{r}
# INI SAMA DENGAN PERCOBAAN 5, THRESHOLD NYA SAMA DINAIKIN MENJADI 0.6, TAPI RUNTIME AWAL DIHAPUS. UNTUK VALIDASI
# EXPERIMENT 7
# USING TREMO Calibration
# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v9.csv')

# Plot the bar chart with the filtered dataset
df_predicted %>%
  ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
  geom_bar() +  # Create a bar chart
  theme_minimal() +  # Use a minimal theme for aesthetics
  labs(title = "Count of Emotions in Dataset",
       x = "Emotion Category",
       y = "Frequency") +  # Add chart labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability

```

```{r}
# INI SAMA DENGAN PERCOBAAN 5, TAPI DIREFACTORING UNTUK MENGHASILKAN DATA TRAINING BERT DENGAN TREMO YANG KONSISTEN
# EXPERIMENT 8
# USING TREMO Calibration
# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v10.csv')

# Plot the bar chart with the filtered dataset
df_predicted %>%
  ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
  geom_bar() +  # Create a bar chart
  theme_minimal() +  # Use a minimal theme for aesthetics
  labs(title = "Count of Emotions in Dataset",
       x = "Emotion Category",
       y = "Frequency") +  # Add chart labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability

```

```{r}
# INI SAMA DENGAN PERCOBAAN 8, TAPI DIULANG TRAINING BERT DENGAN TREMO NYA
# EXPERIMENT 9
# USING TREMO Calibration
# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v11.csv')

# Plot the bar chart with the filtered dataset
df_predicted %>%
  ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
  geom_bar() +  # Create a bar chart
  theme_minimal() +  # Use a minimal theme for aesthetics
  labs(title = "Count of Emotions in Dataset",
       x = "Emotion Category",
       y = "Frequency") +  # Add chart labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability

```

```{r}
# INI SAMA DENGAN PERCOBAAN 9, TAPI DENGAN CODE BARU
# EXPERIMENT 10
# USING TREMO Calibration
# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v12.csv')

# Plot the bar chart with the filtered dataset
df_predicted %>%
  ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
  geom_bar() +  # Create a bar chart
  theme_minimal() +  # Use a minimal theme for aesthetics
  labs(title = "Count of Emotions in Dataset",
       x = "Emotion Category",
       y = "Frequency") +  # Add chart labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability

```

```{r}
# INI SAMA DENGAN PERCOBAAN 10, UNTUK VERIFIKASI
# EXPERIMENT 11
# USING TREMO Calibration
# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v13.csv')

# Plot the bar chart with the filtered dataset
df_predicted %>%
  ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
  geom_bar() +  # Create a bar chart
  theme_minimal() +  # Use a minimal theme for aesthetics
  labs(title = "Count of Emotions in Dataset",
       x = "Emotion Category",
       y = "Frequency") +  # Add chart labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability

```

```{r}
# INI SAMA DENGAN PERCOBAAN 10 DAN 11, DENGAN MODEL TRAINING BARU UNTUK VERIFIKASI
# EXPERIMENT 12
# USING TREMO Calibration
# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Plot the bar chart with the filtered dataset
df_predicted %>%
  ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
  geom_bar() +  # Create a bar chart
  theme_minimal() +  # Use a minimal theme for aesthetics
  labs(title = "Count of Emotions in Dataset",
       x = "Emotion Category",
       y = "Frequency") +  # Add chart labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability

```

```{r}
# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Exclude 'Ambigious' category and calculate the count for each remaining category
emotion_counts <- df_count %>%
  group_by(emotion) %>%
  summarise(Count = n())

# Print the counts
print(emotion_counts)

```

```{r}
# Load the libraries
library(ggplot2)
library(dplyr)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Ensure 'emotion' is a factor
df_predicted$emotion <- as.factor(df_predicted$emotion)

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Creating the scatter plot with custom colors
ggplot(df_predicted, aes(x = date, y = emotion, color = emotion)) +
  geom_point(position = position_jitter(width = 0, height = 0.1), alpha = 0.5) +
  scale_color_manual(values = colors) +  # Apply the custom colors
  theme_minimal() +
  labs(title = "Scatter Plot of Emotions Over Time",
       x = "Date",
       y = "Emotion") +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) # Rotate x-axis labels for better visibility
```

```{r}
# Load the libraries
library(ggplot2)
library(dplyr)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Ensure 'emotion' is a factor
df_predicted$emotion <- as.factor(df_predicted$emotion)

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Filter data to only include dates from June 1, 2021 to December 31, 2021
df_predicted_filtered <- df_predicted %>%
  filter(date >= as.Date("2021-06-01") & date <= as.Date("2021-12-31"))

# Manually setting the breaks to include only months from June 2021 to December 2021
monthly_breaks <- seq(from = as.Date("2021-06-01"), to = as.Date("2021-12-31"), by = "month")

# Creating the scatter plot with custom colors
ggplot(df_predicted_filtered, aes(x = date, y = emotion, color = emotion)) +
  geom_point(position = position_jitter(width = 0, height = 0.1), alpha = 0.5) +
  scale_color_manual(values = colors) +  # Apply the custom colors
  scale_x_date(limits = as.Date(c("2021-06-01", "2021-12-31")), breaks = monthly_breaks, date_labels = "%b %Y") +
  theme_minimal() +
  labs(title = "Scatter Plot of Emotions Over Time (June-Dec 2021)",
       x = "Date",
       y = "Emotion") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for better visibility
```

```{r}
# Load the libraries
library(ggplot2)
library(dplyr)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Ensure 'emotion' is a factor
df_predicted$emotion <- as.factor(df_predicted$emotion)

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Filter data to only include dates up to December 31, 2022
df_predicted_filtered <- df_predicted %>%
  filter(date >= as.Date("2022-01-01") & date <= as.Date("2022-12-31"))

# Manually setting the breaks to include only months in 2022
monthly_breaks <- seq(from = as.Date("2022-01-01"), to = as.Date("2022-12-31"), by = "month")

# Creating the scatter plot with custom colors
ggplot(df_predicted_filtered, aes(x = date, y = emotion, color = emotion)) +
  geom_point(position = position_jitter(width = 0, height = 0.1), alpha = 0.5) +
  scale_color_manual(values = colors) +  # Apply the custom colors
  scale_x_date(limits = as.Date(c("2022-01-01", "2022-12-31")), breaks = monthly_breaks, date_labels = "%b %Y") +
  theme_minimal() +
  labs(title = "Scatter Plot of Emotions Over Time (2022)",
       x = "Date",
       y = "Emotion") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for better visibility
```



### FINAL CODE FINAL CODE FINAL CODE FINAL CODE
### FINAL CODe FINAL CODE FINAL CODe FINAL CODE
### FINAL CODE FINAL CODE FINAL CODE FINAL CODE
### FINAL CODe FINAL CODE FINAL CODe FINAL CODE
### FINAL CODE FINAL CODE FINAL CODE FINAL CODE
### FINAL CODe FINAL CODE FINAL CODe FINAL CODE

```{r}
# INI SAMA DENGAN PERCOBAAN 12, DENGAN MEMECAH CHART MENJADI TAHUN 2021 DAN 2022 
# SEKALIGUS KOMBINASI CHART TAHUN 2021 SAMPAI 2022

# EXPERIMENT 13
# USING TREMO Calibration

# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Filter the dataset by year and get rid of the ambiguous emotions
df_predicted_2021 <- df_predicted %>% filter(year == 2021 & emotion != "ambiguous")
df_predicted_2022 <- df_predicted %>% filter(year == 2022 & emotion != "ambiguous")
df_predicted_combined <- df_predicted %>% filter(emotion != "ambiguous")

# Function to create bar chart
create_bar_chart <- function(data, title) {
  data %>%
    ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
    geom_bar() +  # Create a bar chart
    theme_minimal() +  # Use a minimal theme for aesthetics
    labs(title = title,
         x = "Emotion Category",
         y = "Frequency") +  # Add chart labels
    theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for readability
}

# Plot the bar charts for each year and the combined years
plot_2021 <- create_bar_chart(df_predicted_2021, "Count of Emotions in Dataset - 2021")
plot_2022 <- create_bar_chart(df_predicted_2022, "Count of Emotions in Dataset - 2022")
plot_combined <- create_bar_chart(df_predicted_combined, "Count of Emotions in Dataset - 2021 & 2022")

# Display the plots
print(plot_2021)
print(plot_2022)
print(plot_combined)

```

```{r}
# VERSI THRESOLD 0.6
# INI SAMA DENGAN PERCOBAAN 13, HANYA MENGUBAH WARNA BARNYA MENJADI BIRU
# SEKALIGUS KOMBINASI CHART TAHUN 2021 SAMPAI 2022

# EXPERIMENT 14
# USING TREMO Calibration

# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Filter the dataset by year and get rid of the ambiguous emotions
df_predicted_2021 <- df_predicted %>% filter(year == 2021 & emotion != "ambiguous")
df_predicted_2022 <- df_predicted %>% filter(year == 2022 & emotion != "ambiguous")
df_predicted_combined <- df_predicted %>% filter(emotion != "ambiguous")

# Function to create bar chart with steelblue color
create_bar_chart <- function(data, title) {
  data %>%
    ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
    geom_bar(fill = "steelblue", color = "black") +  # Fill bars with steelblue, add black border
    theme_minimal() +  # Use a minimal theme for aesthetics
    labs(title = title,
         x = "Emotion Category",
         y = "Frequency") +  # Add chart labels
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5))  # Rotate x-axis labels for readability
}

# Plot the bar charts for each year and the combined years
plot_2021 <- create_bar_chart(df_predicted_2021, "Count of Emotions in Dataset - 2021")
plot_2022 <- create_bar_chart(df_predicted_2022, "Count of Emotions in Dataset - 2022")
plot_combined <- create_bar_chart(df_predicted_combined, "Count of Emotions in Dataset - 2021 & 2022")

# Display the plots
print(plot_2021)
print(plot_2022)
print(plot_combined)
```

```{r}
# VERSI THRESOLD 0.5
# INI SAMA DENGAN PERCOBAAN 13, HANYA MENGUBAH WARNA BARNYA MENJADI BIRU
# SEKALIGUS KOMBINASI CHART TAHUN 2021 SAMPAI 2022

# EXPERIMENT 14
# USING TREMO Calibration

# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v0-5.csv')

# Filter the dataset by year and get rid of the ambiguous emotions
df_predicted_2021 <- df_predicted %>% filter(year == 2021 & emotion != "ambiguous")
df_predicted_2022 <- df_predicted %>% filter(year == 2022 & emotion != "ambiguous")
df_predicted_combined <- df_predicted %>% filter(emotion != "ambiguous")

# Function to create bar chart with steelblue color
create_bar_chart <- function(data, title) {
  data %>%
    ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
    geom_bar(fill = "steelblue", color = "black") +  # Fill bars with steelblue, add black border
    theme_minimal() +  # Use a minimal theme for aesthetics
    labs(title = title,
         x = "Emotion Category",
         y = "Frequency") +  # Add chart labels
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5))  # Rotate x-axis labels for readability
}

# Plot the bar charts for each year and the combined years
plot_2021 <- create_bar_chart(df_predicted_2021, "Count of Emotions in Dataset - 2021")
plot_2022 <- create_bar_chart(df_predicted_2022, "Count of Emotions in Dataset - 2022")
plot_combined <- create_bar_chart(df_predicted_combined, "Count of Emotions in Dataset - 2021 & 2022")

# Display the plots
print(plot_2021)
print(plot_2022)
print(plot_combined)
```

```{r}
# VERSI THRESOLD 0.7
# INI SAMA DENGAN PERCOBAAN 13, HANYA MENGUBAH WARNA BARNYA MENJADI BIRU
# SEKALIGUS KOMBINASI CHART TAHUN 2021 SAMPAI 2022

# EXPERIMENT 14
# USING TREMO Calibration

# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v0-7.csv')

# Filter the dataset by year and get rid of the ambiguous emotions
df_predicted_2021 <- df_predicted %>% filter(year == 2021 & emotion != "ambiguous")
df_predicted_2022 <- df_predicted %>% filter(year == 2022 & emotion != "ambiguous")
df_predicted_combined <- df_predicted %>% filter(emotion != "ambiguous")

# Function to create bar chart with steelblue color
create_bar_chart <- function(data, title) {
  data %>%
    ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
    geom_bar(fill = "steelblue", color = "black") +  # Fill bars with steelblue, add black border
    theme_minimal() +  # Use a minimal theme for aesthetics
    labs(title = title,
         x = "Emotion Category",
         y = "Frequency") +  # Add chart labels
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5))  # Rotate x-axis labels for readability
}

# Plot the bar charts for each year and the combined years
plot_2021 <- create_bar_chart(df_predicted_2021, "Count of Emotions in Dataset - 2021")
plot_2022 <- create_bar_chart(df_predicted_2022, "Count of Emotions in Dataset - 2022")
plot_combined <- create_bar_chart(df_predicted_combined, "Count of Emotions in Dataset - 2021 & 2022")

# Display the plots
print(plot_2021)
print(plot_2022)
print(plot_combined)
```

```{r}
# INI SAMA DENGAN PERCOBAAN 14, HANYA MENGUBAH KUALITAS IMAGE MENJADI 300 DPI
# SEKALIGUS KOMBINASI CHART TAHUN 2021 SAMPAI 2022

# EXPERIMENT 15
# USING TREMO Calibration

# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Filter the dataset by year and get rid of the ambiguous emotions
df_predicted_2021 <- df_predicted %>% filter(year == 2021 & emotion != "ambiguous")
df_predicted_2022 <- df_predicted %>% filter(year == 2022 & emotion != "ambiguous")
df_predicted_combined <- df_predicted %>% filter(emotion != "ambiguous")

# Function to create bar chart with steelblue color
create_bar_chart <- function(data, title) {
  data %>%
    ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
    geom_bar(fill = "steelblue", color = "black") +  # Fill bars with steelblue, add black border
    theme_minimal() +  # Use a minimal theme for aesthetics
    labs(title = title,
         x = "Emotion Category",
         y = "Frequency") +  # Add chart labels
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5))  # Rotate x-axis labels for readability
}# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Filter the dataset by year and get rid of the ambiguous emotions
df_predicted_2021 <- df_predicted %>% filter(year == 2021 & emotion != "ambiguous")
df_predicted_2022 <- df_predicted %>% filter(year == 2022 & emotion != "ambiguous")
df_predicted_combined <- df_predicted %>% filter(emotion != "ambiguous")

# Function to create bar chart with steelblue color
create_bar_chart <- function(data, title) {
  data %>%
    ggplot(aes(x = emotion)) +  # Specify the column for the x-axis
    geom_bar(fill = "steelblue", color = "black") +  # Fill bars with steelblue, add black border
    theme_minimal() +  # Use a minimal theme for aesthetics
    labs(title = title,
         x = "Emotion Category",
         y = "Frequency") +  # Add chart labels
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5))  # Rotate x-axis labels for readability
}

# Plot the bar charts for each year and the combined years
plot_2021 <- create_bar_chart(df_predicted_2021, "Count of Emotions in Dataset - 2021")
plot_2022 <- create_bar_chart(df_predicted_2022, "Count of Emotions in Dataset - 2022")
plot_combined <- create_bar_chart(df_predicted_combined, "Count of Emotions in Dataset - 2021 & 2022")

# Define the output folder
output_folder <- "300dpi"

# Save the plots as TIFF images with 300 DPI
ggsave(
  filename = file.path(output_folder, "plot_2021.tiff"),  # File name for 2021 plot
  plot = plot_2021,           # Plot object
  device = "tiff",            # Save as TIFF
  dpi = 300,                  # Resolution in DPI
  width = 8, height = 6,      # Dimensions in inches
  units = "in"
)

ggsave(
  filename = file.path(output_folder, "plot_2022.tiff"),  # File name for 2022 plot
  plot = plot_2022,           # Plot object
  device = "tiff",            # Save as TIFF
  dpi = 300,                  # Resolution in DPI
  width = 8, height = 6,      # Dimensions in inches
  units = "in"
)

ggsave(
  filename = file.path(output_folder, "plot_combined.tiff"),  # File name for combined plot
  plot = plot_combined,           # Plot object
  device = "tiff",                # Save as TIFF
  dpi = 300,                      # Resolution in DPI
  width = 8, height = 6,          # Dimensions in inches
  units = "in"
)

# Display the plots
print(plot_2021)
print(plot_2022)
print(plot_combined)
```

```{r}
# VERSI THRESOLD 0.6
# INI SAMA DENGAN PERCOBAAN 15, HANYA MENGUBAH KUALITAS IMAGE MENJADI 600 DPI
# SEKALIGUS KOMBINASI CHART TAHUN 2021 SAMPAI 2022

# EXPERIMENT 16
# USING TREMO Calibration

# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Filter the dataset by year and get rid of the ambiguous emotions
df_predicted_combined <- df_predicted %>% filter(emotion != "ambiguous")

# Define custom colors for emotions
colors <- c("anger" = "red", 
            "disgust" = "green", 
            "fear" = "purple", 
            "happy" = "yellow", 
            "sadness" = "blue", 
            "surprise" = "orange")

# Function to create bar chart with custom colors, no title, and no legend
create_bar_chart_no_title_no_legend <- function(data, colors) {
  data %>%
    ggplot(aes(x = emotion, fill = emotion)) +  # Specify the column for the x-axis and fill by emotion
    geom_bar(color = "black") +  # Add black border around bars
    scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
    theme_minimal() +  # Use a minimal theme for aesthetics
    labs(x = "Emotion Category",
         y = "Frequency") +  # Add chart labels without title
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5),  # Rotate x-axis labels for readability
          legend.position = "none")  # Remove the legend
}

# Create the plot without the title and legend
plot_combined <- create_bar_chart_no_title_no_legend(df_predicted_combined, colors)

# Define the output folder
output_folder <- "300dpi"

# Ensure the output folder exists
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
}

# Save the plot as a TIFF file
ggsave(
  filename = file.path(output_folder, "Figure 7.tiff"),  # Save as Figure 7.tiff in the 300dpi folder
  plot = plot_combined,           # Plot object
  device = "tiff",                # Save as TIFF format
  dpi = 600,                      # Resolution in DPI
  width = 8, height = 6,          # Dimensions in inches
  units = "in"                    # Specify units
)

# Optionally print the plot to display it in the R environment
print(plot_combined)
```

```{r}
# VERSI THRESOLD 0.5
# INI SAMA DENGAN PERCOBAAN 15, HANYA MENGUBAH KUALITAS IMAGE MENJADI 600 DPI
# SEKALIGUS KOMBINASI CHART TAHUN 2021 SAMPAI 2022

# EXPERIMENT 16
# USING TREMO Calibration

# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v0-5.csv')

# Filter the dataset by year and get rid of the ambiguous emotions
df_predicted_combined <- df_predicted %>% filter(emotion != "ambiguous")

# Define custom colors for emotions
colors <- c("anger" = "red", 
            "disgust" = "green", 
            "fear" = "purple", 
            "happy" = "yellow", 
            "sadness" = "blue", 
            "surprise" = "orange")

# Function to create bar chart with custom colors, no title, and no legend
create_bar_chart_no_title_no_legend <- function(data, colors) {
  data %>%
    ggplot(aes(x = emotion, fill = emotion)) +  # Specify the column for the x-axis and fill by emotion
    geom_bar(color = "black") +  # Add black border around bars
    scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
    theme_minimal() +  # Use a minimal theme for aesthetics
    labs(x = "Emotion Category",
         y = "Frequency") +  # Add chart labels without title
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5),  # Rotate x-axis labels for readability
          legend.position = "none")  # Remove the legend
}

# Create the plot without the title and legend
plot_combined <- create_bar_chart_no_title_no_legend(df_predicted_combined, colors)

# Define the output folder
output_folder <- "AAIML-600dpi"

# Ensure the output folder exists
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
}

# Save the plot as a TIFF file
ggsave(
  filename = file.path(output_folder, "Figure 7-05.tiff"),  # Save as Figure 7.tiff in the 300dpi folder
  plot = plot_combined,           # Plot object
  device = "tiff",                # Save as TIFF format
  dpi = 600,                      # Resolution in DPI
  width = 8, height = 6,          # Dimensions in inches
  units = "in"                    # Specify units
)

# Optionally print the plot to display it in the R environment
print(plot_combined)
```

```{r}
# VERSI THRESOLD 0.7
# INI SAMA DENGAN PERCOBAAN 15, HANYA MENGUBAH KUALITAS IMAGE MENJADI 600 DPI
# SEKALIGUS KOMBINASI CHART TAHUN 2021 SAMPAI 2022

# EXPERIMENT 16
# USING TREMO Calibration

# Load the necessary library
library(tidyverse)

# Read the dataset
df_predicted <- read.csv('silentinvasionv4_2021_2022_with_emotions_v0-7.csv')

# Filter the dataset by year and get rid of the ambiguous emotions
df_predicted_combined <- df_predicted %>% filter(emotion != "ambiguous")

# Define custom colors for emotions
colors <- c("anger" = "red", 
            "disgust" = "green", 
            "fear" = "purple", 
            "happy" = "yellow", 
            "sadness" = "blue", 
            "surprise" = "orange")

# Function to create bar chart with custom colors, no title, and no legend
create_bar_chart_no_title_no_legend <- function(data, colors) {
  data %>%
    ggplot(aes(x = emotion, fill = emotion)) +  # Specify the column for the x-axis and fill by emotion
    geom_bar(color = "black") +  # Add black border around bars
    scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
    theme_minimal() +  # Use a minimal theme for aesthetics
    labs(x = "Emotion Category",
         y = "Frequency") +  # Add chart labels without title
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5),  # Rotate x-axis labels for readability
          legend.position = "none")  # Remove the legend
}

# Create the plot without the title and legend
plot_combined <- create_bar_chart_no_title_no_legend(df_predicted_combined, colors)

# Define the output folder
output_folder <- "AAIML-600dpi"

# Ensure the output folder exists
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
}

# Save the plot as a TIFF file
ggsave(
  filename = file.path(output_folder, "Figure 7-07.tiff"),  # Save as Figure 7.tiff in the 300dpi folder
  plot = plot_combined,           # Plot object
  device = "tiff",                # Save as TIFF format
  dpi = 600,                      # Resolution in DPI
  width = 8, height = 6,          # Dimensions in inches
  units = "in"                    # Specify units
)

# Optionally print the plot to display it in the R environment
print(plot_combined)
```

```{r}
# VERSI THRESOLD 0.6
# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Exclude 'Ambigious' category and calculate the count for each remaining category
emotion_counts <- df_count %>%
  filter(emotion != "ambiguous") %>%  # Exclude 'Ambiguous' category
  group_by(emotion) %>%
  summarise(Count = n())

# Print the counts
print(emotion_counts)

```

```{r}
# VERSI THRESOLD 0.5
# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v0-5.csv')

# Exclude 'Ambigious' category and calculate the count for each remaining category
emotion_counts <- df_count %>%
  filter(emotion != "ambiguous") %>%  # Exclude 'Ambiguous' category
  group_by(emotion) %>%
  summarise(Count = n())

# Print the counts
print(emotion_counts)

```

```{r}
# VERSI THRESOLD 0.7
# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v0-7.csv')

# Exclude 'Ambigious' category and calculate the count for each remaining category
emotion_counts <- df_count %>%
  filter(emotion != "ambiguous") %>%  # Exclude 'Ambiguous' category
  group_by(emotion) %>%
  summarise(Count = n())

# Print the counts
print(emotion_counts)

```

```{r}
# KOMBINASI TAHUN 2021 SAMPAI DENGAN TAHUN 2022

# Load the libraries
library(ggplot2)
library(dplyr)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Ensure 'emotion' is a factor
df_predicted$emotion <- as.factor(df_predicted$emotion)

# Filter out rows where 'emotion' is "ambiguous"
df_filtered <- df_predicted %>% filter(emotion != "ambiguous")

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Creating the scatter plot with custom colors
ggplot(df_filtered, aes(x = date, y = emotion, color = emotion)) +
  geom_point(position = position_jitter(width = 0, height = 0.1), alpha = 0.5) +
  scale_color_manual(values = colors) +  # Apply the custom colors
  theme_minimal() +
  labs(title = "Scatter Plot of Emotions Over Time",
       x = "Month",
       y = "Emotion") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for better visibility
```

```{r}
# HANYA TAHUN 2021

# Load the libraries
library(ggplot2)
library(dplyr)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Ensure 'emotion' is a factor
df_predicted$emotion <- as.factor(df_predicted$emotion)

# Filter out rows where 'emotion' is "ambiguous"
df_filtered <- df_predicted %>% filter(emotion != "ambiguous")

# Filter data to only include dates from June 1, 2021, to December 31, 2021
df_filtered <- df_filtered %>%
  filter(date >= as.Date("2021-06-01") & date <= as.Date("2021-12-31"))

# Manually setting the breaks to include only months from June 2021 to December 2021
monthly_breaks <- seq(from = as.Date("2021-06-01"), to = as.Date("2021-12-31"), by = "month")

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Creating the scatter plot with custom colors
ggplot(df_filtered, aes(x = date, y = emotion, color = emotion)) +
  geom_point(position = position_jitter(width = 0, height = 0.1), alpha = 0.5) +
  scale_color_manual(values = colors) +  # Apply the custom colors
  scale_x_date(limits = as.Date(c("2021-06-01", "2021-12-31")), breaks = monthly_breaks, date_labels = "%b %Y") +
  theme_minimal() +
  labs(title = "Scatter Plot of Emotions Over Time (June-Dec 2021)",
       x = "Month",
       y = "Emotion") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for better visibility
```

```{r}
# Generate Total Monthly Emotion Counts for 2021

# Load the libraries
library(ggplot2)
library(dplyr)
library(lubridate)  # For date handling

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Filter out rows where 'emotion' is "ambiguous"
df_filtered <- df_predicted %>%
  filter(emotion != "ambiguous")

# Filter data to only include dates within the year 2021
df_filtered <- df_filtered %>%
  filter(date >= as.Date("2021-01-01") & date <= as.Date("2021-12-31"))

# Summarize the total count of emotions by month
df_summary <- df_filtered %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(month) %>%
  summarise(total_count = n(), .groups = 'drop')

# Create the bar chart
ggplot(df_summary, aes(x = month, y = total_count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  scale_x_date(breaks = seq(as.Date("2021-01-01"), as.Date("2021-12-31"), by = "month"), date_labels = "%b %Y") +
  theme_minimal() +
  labs(title = "Total Emotion Counts per Month in 2021",
       x = "Month",
       y = "Total Emotion Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better visibility
```


```{r}
# KALKULASI TAHUN 2021
# Dengan menampilkan semua emosi

# Generate Monthly Counts for Selected Emotions in 2021

# Load the libraries
library(ggplot2)
library(dplyr)
library(lubridate)  # For date handling

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Filter out rows where 'emotion' is "ambiguous" and keep only selected emotions
df_filtered <- df_predicted %>%
  filter(emotion %in% c("anger", "disgust", "fear", "happy", "sadness", "surprise"))

# Filter data to only include dates within the year 2021
df_filtered <- df_filtered %>%
  filter(date >= as.Date("2021-01-01") & date <= as.Date("2021-12-31"))

# Summarize the count of each selected emotion by month
df_summary <- df_filtered %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(month, emotion) %>%
  summarise(count = n(), .groups = 'drop')

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Create the bar chart
ggplot(df_summary, aes(x = month, y = count, fill = emotion)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
  scale_x_date(breaks = seq(as.Date("2021-01-01"), as.Date("2021-12-31"), by = "month"), date_labels = "%b %Y") +
  theme_minimal() +
  labs(title = "Monthly Emotion Count Over Time (June-December 2021)",
       x = "Month",
       y = "Emotion Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better visibility
```

```{r}
# KALKULASI TAHUN 2021 MENGHILANGKAN TAHUNNYA SAJA
# Dengan menampilkan semua emosi

# Generate Monthly Counts for Selected Emotions in 2021

# Load the libraries
library(ggplot2)
library(dplyr)
library(lubridate)  # For date handling

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Filter out rows where 'emotion' is "ambiguous" and keep only selected emotions
df_filtered <- df_predicted %>%
  filter(emotion %in% c("anger", "disgust", "fear", "happy", "sadness", "surprise"))

# Filter data to only include dates within the year 2021
df_filtered <- df_filtered %>%
  filter(date >= as.Date("2021-01-01") & date <= as.Date("2021-12-31"))

# Summarize the count of each selected emotion by month
df_summary <- df_filtered %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(month, emotion) %>%
  summarise(count = n(), .groups = 'drop')

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Create the bar chart
ggplot(df_summary, aes(x = month, y = count, fill = emotion)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
  scale_x_date(breaks = seq(as.Date("2021-01-01"), as.Date("2021-12-31"), by = "month"), date_labels = "%b") +
  theme_minimal() +
  labs(title = "Monthly Emotion Count Over Time (June-December 2021)",
       x = "Month",
       y = "Emotion Count") +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))  # Rotate x-axis labels for better visibility
```

```{r}
# KALKULASI TAHUN 2021 DENGAN PERUBAHAN GAMBAR 300 DPI
# Dengan menampilkan semua emosi

# Load the libraries
library(ggplot2)
library(dplyr)
library(lubridate)

# Define the output folder
output_folder <- "300dpi"

# Ensure the output folder exists
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
}

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Filter out rows where 'emotion' is "ambiguous" and keep only selected emotions
df_filtered <- df_predicted %>%
  filter(emotion %in% c("anger", "disgust", "fear", "happy", "sadness", "surprise"))

# Filter data to only include dates within the year 2021
df_filtered <- df_filtered %>%
  filter(date >= as.Date("2021-01-01") & date <= as.Date("2021-12-31"))

# Summarize the count of each selected emotion by month
df_summary <- df_filtered %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(month, emotion) %>%
  summarise(count = n(), .groups = 'drop')

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Create the plot
plot <- ggplot(df_summary, aes(x = month, y = count, fill = emotion)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
  scale_x_date(breaks = seq(as.Date("2021-01-01"), as.Date("2021-12-31"), by = "month"), date_labels = "%b") +
  theme_minimal() +
  labs(title = "Monthly Emotion Count Over Time (June-December 2021)",
       x = "Month",
       y = "Emotion Count") +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))  # Rotate x-axis labels for better visibility

# Save the plot as a TIFF file
ggsave(
  filename = file.path(output_folder, "Figure 8.tiff"),  # Save as Figure 8.tiff in the 300dpi folder
  plot = plot,                     # The plot object
  device = "tiff",                 # Save as TIFF format
  dpi = 300,                       # 300 DPI resolution
  width = 8, height = 6,           # Dimensions in inches
  units = "in"                     # Specify units
)

# Optionally print the plot to display it in the R environment
print(plot)
```

```{r}
# KALKULASI TAHUN 2021 DENGAN PERUBAHAN GAMBAR 600 DPI DAN MENGHILANGKAN CAPTION GAMBAR
# Dengan menampilkan semua emosi

# Load the libraries
library(ggplot2)
library(dplyr)
library(lubridate)

# Define the output folder
output_folder <- "300dpi"

# Ensure the output folder exists
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
}

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Filter out rows where 'emotion' is "ambiguous" and keep only selected emotions
df_filtered <- df_predicted %>%
  filter(emotion %in% c("anger", "disgust", "fear", "happy", "sadness", "surprise"))

# Filter data to only include dates within the year 2021
df_filtered <- df_filtered %>%
  filter(date >= as.Date("2021-01-01") & date <= as.Date("2021-12-31"))

# Summarize the count of each selected emotion by month
df_summary <- df_filtered %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(month, emotion) %>%
  summarise(count = n(), .groups = 'drop')

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Create the plot without the title
plot <- ggplot(df_summary, aes(x = month, y = count, fill = emotion)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
  scale_x_date(breaks = seq(as.Date("2021-01-01"), as.Date("2021-12-31"), by = "month"), date_labels = "%b") +
  theme_minimal() +
  labs(x = "Month", y = "Emotion Count") +  # Labels without title
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))  # Rotate x-axis labels for better visibility

# Save the plot as a TIFF file
ggsave(
  filename = file.path(output_folder, "Figure 8.tiff"),  # Save as Figure 8.tiff in the 300dpi folder
  plot = plot,                     # The plot object
  device = "tiff",                 # Save as TIFF format
  dpi = 600,                       # 600 DPI resolution
  width = 8, height = 6,           # Dimensions in inches
  units = "in"                     # Specify units
)

# Optionally print the plot to display it in the R environment
print(plot)
```


```{r}
# Kalkulasi tahun 2021

# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Convert date column to Date type if it's not already
df_count <- df_count %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"))  # replace `date_column` with actual date column name

# Filter for the year 2021, exclude 'Ambiguous' category, and group by month
monthly_emotion_count_2021 <- df_count %>%
  filter(format(date, "%Y") == "2021", emotion != "ambiguous") %>%
  mutate(month = format(date, "%Y-%m")) %>%  # Extract year-month format
  group_by(month) %>%
  summarise(Total_Emotion_Count = n(), .groups = "drop")

# Print the total emotion count per month for 2021
print(monthly_emotion_count_2021)
```

```{r}
# Kalkulasi tahun 2021

# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Convert date column to Date type if it's not already
df_count <- df_count %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"))  # replace `date_column` with actual date column name

# Filter for the year 2021, exclude 'Ambiguous' category, and group by month
monthly_emotion_count_2021 <- df_count %>%
  filter(format(date, "%Y") == "2021", emotion != "ambiguous") %>%
  mutate(month = format(date, "%Y-%m")) %>%  # Extract year-month format
  group_by(month) %>%
  summarise(Total_Emotion_Count = n(), .groups = "drop")

# Calculate total emotion count for the entire year 2021
total_emotion_count_2021 <- sum(monthly_emotion_count_2021$Total_Emotion_Count)

# Add a percentage column with one decimal place
monthly_emotion_count_2021 <- monthly_emotion_count_2021 %>%
  mutate(Percentage = round((Total_Emotion_Count / total_emotion_count_2021) * 100, 1))

# Print the percentage of total emotions per month for 2021
print(monthly_emotion_count_2021)
```

```{r}
# Kalkulasi tahun 2021

# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Convert date column to Date type if it's not already
df_count <- df_count %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"))  # replace `date_column` with actual date column name

# Filter for the year 2021 and exclude 'Ambiguous' category, then group by emotion
annual_emotion_count_2021 <- df_count %>%
  filter(format(date, "%Y") == "2021", emotion != "ambiguous") %>%
  group_by(emotion) %>%
  summarise(Emotion_Count = n(), .groups = "drop")

# Calculate the total count of all emotions for the entire year 2021
total_emotions_2021 <- sum(annual_emotion_count_2021$Emotion_Count)

# Add a percentage column for each emotion based on the annual total
annual_emotion_count_2021 <- annual_emotion_count_2021 %>%
  mutate(Percentage = round((Emotion_Count / total_emotions_2021) * 100, 1))

# Print the result
print(annual_emotion_count_2021)
```

```{r}
# FOKUS PADA DATA BULAN JULI DAN DESEMBER 2021

# Load necessary libraries
library(ggplot2)
library(dplyr)
library(lubridate)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Filter out rows where 'emotion' is "ambiguous" and keep only selected emotions
df_filtered <- df_predicted %>%
  filter(emotion %in% c("anger", "disgust", "fear", "happy", "sadness", "surprise"))

# Filter data to only include July 1–31 and December 1–31 of 2021
df_filtered_june_december <- df_filtered %>%
  filter((date >= as.Date("2021-07-01") & date <= as.Date("2021-07-31")) |
           (date >= as.Date("2021-12-01") & date <= as.Date("2021-12-31")))

# Summarize the count of each selected emotion for June and December
df_summary <- df_filtered_june_december %>%
  mutate(month = format(date, "%Y-%m")) %>%
  group_by(month, emotion) %>%
  summarise(count = n(), .groups = 'drop')

# Calculate the total counts per month for percentage calculation
df_percentage <- df_summary %>%
  group_by(month) %>%
  mutate(total_count = sum(count),
         percentage = (count / total_count) * 100) %>%
  ungroup()

# Print the data for verification
print(df_percentage)

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Create the bar chart showing percentages for July and December
ggplot(df_percentage, aes(x = emotion, y = percentage, fill = emotion)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
  facet_wrap(~ month, labeller = as_labeller(function(x) format(as.Date(paste0(x, "-01")), "%B"))) +
  theme_minimal() +
  labs(title = "Emotion Percentage Distribution for July and December 2021",
       x = "Emotion",
       y = "Percentage (%)") +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))  # Adjust x-axis labels
```

```{r}
# FOKUS PADA DATA BULAN JULI DAN DESEMBER 2021
# Dengan perubahan gambar 600 dpi dan menghilangkan caption gambar

# Load necessary libraries
library(ggplot2)
library(dplyr)
library(lubridate)

# Define the output folder
output_folder <- "300dpi"

# Ensure the output folder exists
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
}

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Filter out rows where 'emotion' is "ambiguous" and keep only selected emotions
df_filtered <- df_predicted %>%
  filter(emotion %in% c("anger", "disgust", "fear", "happy", "sadness", "surprise"))

# Filter data to only include July 1–31 and December 1–31 of 2021
df_filtered_june_december <- df_filtered %>%
  filter((date >= as.Date("2021-07-01") & date <= as.Date("2021-07-31")) |
           (date >= as.Date("2021-12-01") & date <= as.Date("2021-12-31")))

# Summarize the count of each selected emotion for June and December
df_summary <- df_filtered_june_december %>%
  mutate(month = format(date, "%Y-%m")) %>%
  group_by(month, emotion) %>%
  summarise(count = n(), .groups = 'drop')

# Calculate the total counts per month for percentage calculation
df_percentage <- df_summary %>%
  group_by(month) %>%
  mutate(total_count = sum(count),
         percentage = (count / total_count) * 100) %>%
  ungroup()

# Print the data for verification
print(df_percentage)

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Create the plot without the legend
plot <- ggplot(df_percentage, aes(x = emotion, y = percentage, fill = emotion)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
  facet_wrap(~ month, labeller = as_labeller(function(x) format(as.Date(paste0(x, "-01")), "%B"))) +
  theme_minimal() +
  labs(x = "Emotion", y = "Percentage (%)") +  # Labels without title
  theme(
    axis.text.x = element_text(angle = 0, hjust = 0.5),  # Adjust x-axis labels
    legend.position = "none"  # Remove the legend
  )

# Save the plot as a TIFF file
ggsave(
  filename = file.path(output_folder, "Figure 10.tiff"),  # Save as Figure 10.tiff in the 300dpi folder
  plot = plot,                     # The plot object
  device = "tiff",                 # Save as TIFF format
  dpi = 600,                       # 600 DPI resolution
  width = 8, height = 6,           # Dimensions in inches
  units = "in"                     # Specify units
)

# Optionally print the plot to display it in the R environment
print(plot)
```


```{r}
# HANYA TAHUN 2022

# Load the libraries
library(ggplot2)
library(dplyr)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Ensure 'emotion' is a factor
df_predicted$emotion <- as.factor(df_predicted$emotion)

# Filter out rows where 'emotion' is "ambiguous"
df_filtered <- df_predicted %>% filter(emotion != "ambiguous")

# Filter data to only include dates from January 1, 2022, to December 31, 2022
df_filtered <- df_filtered %>%
  filter(date >= as.Date("2022-01-01") & date <= as.Date("2022-12-31"))

# Manually setting the breaks to include only months in 2022
monthly_breaks <- seq(from = as.Date("2022-01-01"), to = as.Date("2022-12-31"), by = "month")

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Creating the scatter plot with custom colors
ggplot(df_filtered, aes(x = date, y = emotion, color = emotion)) +
  geom_point(position = position_jitter(width = 0, height = 0.1), alpha = 0.5) +
  scale_color_manual(values = colors) +  # Apply the custom colors
  scale_x_date(limits = as.Date(c("2022-01-01", "2022-12-31")), breaks = monthly_breaks, date_labels = "%b %Y") +
  theme_minimal() +
  labs(title = "Scatter Plot of Emotions Over Time (Jan-Dec 2022)",
       x = "Month",
       y = "Emotion") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate x-axis labels for better visibility
```

```{r}
# KALKULASI TAHUN 2022
# Dengan menampilkan semua emosi

# Generate Monthly Counts for Selected Emotions in 2022

# Load the libraries
library(ggplot2)
library(dplyr)
library(lubridate)  # For date handling

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Filter out rows where 'emotion' is "ambiguous" and keep only selected emotions
df_filtered <- df_predicted %>%
  filter(emotion %in% c("anger", "disgust", "fear", "happy", "sadness", "surprise"))

# Filter data to only include dates within the year 2022
df_filtered <- df_filtered %>%
  filter(date >= as.Date("2022-01-01") & date <= as.Date("2022-12-31"))

# Summarize the count of each selected emotion by month
df_summary <- df_filtered %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(month, emotion) %>%
  summarise(count = n(), .groups = 'drop')

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Create the bar chart
ggplot(df_summary, aes(x = month, y = count, fill = emotion)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
  scale_x_date(breaks = seq(as.Date("2022-01-01"), as.Date("2022-12-31"), by = "month"), date_labels = "%b %Y") +
  theme_minimal() +
  labs(title = "Monthly Emotion Count Over Time (Jan-Dec 2022)",
       x = "Month",
       y = "Emotion Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better visibility
```

```{r}
# NAMA BULANNYA RATA DAN MENGHILANGKAN TAHUN

# Generate Monthly Counts for Selected Emotions in 2022

# Load the libraries
library(ggplot2)
library(dplyr)
library(lubridate)  # For date handling

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Filter out rows where 'emotion' is "ambiguous" and keep only selected emotions
df_filtered <- df_predicted %>%
  filter(emotion %in% c("anger", "disgust", "fear", "happy", "sadness", "surprise"))

# Filter data to only include dates within the year 2022
df_filtered <- df_filtered %>%
  filter(date >= as.Date("2022-01-01") & date <= as.Date("2022-12-31"))

# Summarize the count of each selected emotion by month
df_summary <- df_filtered %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(month, emotion) %>%
  summarise(count = n(), .groups = 'drop')

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Create the bar chart
ggplot(df_summary, aes(x = month, y = count, fill = emotion)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
  scale_x_date(breaks = seq(as.Date("2022-01-01"), as.Date("2022-12-31"), by = "month"), date_labels = "%b") +
  theme_minimal() +
  labs(title = "Monthly Emotion Count Over Time (Jan-Dec 2022)",
       x = "Month",
       y = "Emotion Count") +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))  # Rotate x-axis labels for better visibility
```

```{r}
# KALKULASI TAHUN 2022 DENGAN PERUBAHAN GAMBAR 600 DPI DAN MENGHILANGKAN CAPTION GAMBAR
# Dengan menampilkan semua emosi

# Generate Monthly Counts for Selected Emotions in 2022

# Load the libraries
library(ggplot2)
library(dplyr)
library(lubridate)  # For date handling

# Define the output folder
output_folder <- "300dpi"

# Ensure the output folder exists
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
}

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Filter out rows where 'emotion' is "ambiguous" and keep only selected emotions
df_filtered <- df_predicted %>%
  filter(emotion %in% c("anger", "disgust", "fear", "happy", "sadness", "surprise"))

# Filter data to only include dates within the year 2022
df_filtered <- df_filtered %>%
  filter(date >= as.Date("2022-01-01") & date <= as.Date("2022-12-31"))

# Summarize the count of each selected emotion by month
df_summary <- df_filtered %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(month, emotion) %>%
  summarise(count = n(), .groups = 'drop')

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Create the plot without the title
plot <- ggplot(df_summary, aes(x = month, y = count, fill = emotion)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
  scale_x_date(breaks = seq(as.Date("2022-01-01"), as.Date("2022-12-31"), by = "month"), date_labels = "%b") +
  theme_minimal() +
  labs(x = "Month", y = "Emotion Count") +  # Labels without title
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))  # Rotate x-axis labels for better visibility

# Save the plot as a TIFF file
ggsave(
  filename = file.path(output_folder, "Figure 9.tiff"),  # Save as Figure 9.tiff in the 300dpi folder
  plot = plot,                     # The plot object
  device = "tiff",                 # Save as TIFF format
  dpi = 600,                       # 600 DPI resolution
  width = 8, height = 6,           # Dimensions in inches
  units = "in"                     # Specify units
)

# Optionally print the plot to display it in the R environment
print(plot)
```


```{r}
# Kalkulasi tahun 2022

# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Convert date column to Date type if it's not already
df_count <- df_count %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"))  # replace `date_column` with actual date column name

# Filter for the year 2022, exclude 'Ambiguous' category, and group by month
monthly_emotion_count_2022 <- df_count %>%
  filter(format(date, "%Y") == "2022", emotion != "ambiguous") %>%
  mutate(month = format(date, "%Y-%m")) %>%  # Extract year-month format
  group_by(month) %>%
  summarise(Total_Emotion_Count = n(), .groups = "drop")

# Print the total emotion count per month for 2022
print(monthly_emotion_count_2022)
```

```{r}
# Kalkulasi tahun 2022

# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Convert date column to Date type if it's not already
df_count <- df_count %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"))  # replace `date_column` with actual date column name

# Filter for the year 2022, exclude 'Ambiguous' category, and group by month
monthly_emotion_count_2022 <- df_count %>%
  filter(format(date, "%Y") == "2022", emotion != "ambiguous") %>%
  mutate(month = format(date, "%Y-%m")) %>%  # Extract year-month format
  group_by(month) %>%
  summarise(Total_Emotion_Count = n(), .groups = "drop")

# Calculate total emotion count for the entire year 2022
total_emotion_count_2022 <- sum(monthly_emotion_count_2022$Total_Emotion_Count)

# Add a percentage column with one decimal place
monthly_emotion_count_2022 <- monthly_emotion_count_2022 %>%
  mutate(Percentage = round((Total_Emotion_Count / total_emotion_count_2022) * 100, 1))

# Print the percentage of total emotions per month for 2022
print(monthly_emotion_count_2022)
```

```{r}
# Kalkulasi tahun 2022

# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Convert date column to Date type if it's not already
df_count <- df_count %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"))  # replace `date_column` with actual date column name

# Filter for the year 2022 and exclude 'Ambiguous' category, then group by emotion
annual_emotion_count_2022 <- df_count %>%
  filter(format(date, "%Y") == "2022", emotion != "ambiguous") %>%
  group_by(emotion) %>%
  summarise(Emotion_Count = n(), .groups = "drop")

# Calculate the total count of all emotions for the entire year 2022
total_emotions_2022 <- sum(annual_emotion_count_2022$Emotion_Count)

# Add a percentage column for each emotion based on the annual total
annual_emotion_count_2022 <- annual_emotion_count_2022 %>%
  mutate(Percentage = round((Emotion_Count / total_emotions_2022) * 100, 1))

# Print the result
print(annual_emotion_count_2022)
```

```{r}
# FOKUS PADA DATA BULAN MEI DAN JUNI 2022
# Dengan perubahan gambar 600 DPI

# Load necessary libraries
library(ggplot2)
library(dplyr)
library(lubridate)

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Filter out rows where 'emotion' is "ambiguous" and keep only selected emotions
df_filtered <- df_predicted %>%
  filter(emotion %in% c("anger", "disgust", "fear", "happy", "sadness", "surprise"))

# Filter data to only include May and June of 2022
df_filtered_may_june <- df_filtered %>%
  filter(date >= as.Date("2022-05-01") & date <= as.Date("2022-06-30"))

# Summarize the count of each selected emotion for May and June
df_summary <- df_filtered_may_june %>%
  mutate(month = format(date, "%Y-%m")) %>%
  group_by(month, emotion) %>%
  summarise(count = n(), .groups = 'drop')

# Calculate the total counts per month for percentage calculation
df_percentage <- df_summary %>%
  group_by(month) %>%
  mutate(total_count = sum(count),
         percentage = (count / total_count) * 100) %>%
  ungroup()

# Print the data for verification
print(df_percentage)

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Create the bar chart showing percentages for May and June
ggplot(df_percentage, aes(x = emotion, y = percentage, fill = emotion)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
  facet_wrap(~ month, labeller = as_labeller(function(x) format(as.Date(paste0(x, "-01")), "%B"))) +
  theme_minimal() +
  labs(title = "Emotion Percentage Distribution for May and June 2022",
       x = "Emotion",
       y = "Percentage (%)") +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))  # Adjust x-axis labels
```

```{r}
# FOKUS PADA DATA BULAN MEI DAN JUNI 2022
# Dengan perubahan gambar 600 DPI

# Load necessary libraries
library(ggplot2)
library(dplyr)
library(lubridate)

# Define the output folder
output_folder <- "300dpi"

# Ensure the output folder exists
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
}

# Ensure the 'date' column is in Date format
df_predicted$date <- as.Date(df_predicted$date)

# Filter out rows where 'emotion' is "ambiguous" and keep only selected emotions
df_filtered <- df_predicted %>%
  filter(emotion %in% c("anger", "disgust", "fear", "happy", "sadness", "surprise"))

# Filter data to only include May and June of 2022
df_filtered_may_june <- df_filtered %>%
  filter(date >= as.Date("2022-05-01") & date <= as.Date("2022-06-30"))

# Summarize the count of each selected emotion for May and June
df_summary <- df_filtered_may_june %>%
  mutate(month = format(date, "%Y-%m")) %>%
  group_by(month, emotion) %>%
  summarise(count = n(), .groups = 'drop')

# Calculate the total counts per month for percentage calculation
df_percentage <- df_summary %>%
  group_by(month) %>%
  mutate(total_count = sum(count),
         percentage = (count / total_count) * 100) %>%
  ungroup()

# Print the data for verification
print(df_percentage)

# Define colors for each emotion
colors <- c("anger" = "red", "disgust" = "green", "fear" = "purple", "happy" = "yellow", "sadness" = "blue", "surprise" = "orange")

# Create the plot without the legend
plot <- ggplot(df_percentage, aes(x = emotion, y = percentage, fill = emotion)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = colors) +  # Apply custom colors for each emotion
  facet_wrap(~ month, labeller = as_labeller(function(x) format(as.Date(paste0(x, "-01")), "%B"))) +
  theme_minimal() +
  labs(x = "Emotion", y = "Percentage (%)") +  # Labels without title
  theme(
    axis.text.x = element_text(angle = 0, hjust = 0.5),  # Adjust x-axis labels
    legend.position = "none"  # Remove the legend
  )

# Save the plot as a TIFF file
ggsave(
  filename = file.path(output_folder, "Figure 11.tiff"),  # Save as Figure 11.tiff in the 300dpi folder
  plot = plot,                     # The plot object
  device = "tiff",                 # Save as TIFF format
  dpi = 600,                       # 600 DPI resolution
  width = 8, height = 6,           # Dimensions in inches
  units = "in"                     # Specify units
)

# Optionally print the plot to display it in the R environment
print(plot)
```


```{r}
# Kalkulasi tahun 2021 sampai dengan tahun 2022

# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Convert date column to Date type if it's not already
df_count <- df_count %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"))  # replace `date_column` with actual date column name

# Filter for the years 2021 and 2022, exclude 'Ambiguous' category, and group by month
monthly_emotion_count <- df_count %>%
  filter(format(date, "%Y") %in% c("2021", "2022"), emotion != "ambiguous") %>%
  mutate(month = format(date, "%Y-%m")) %>%  # Extract year-month format
  group_by(month) %>%
  summarise(Total_Emotion_Count = n(), .groups = "drop")

# Calculate the total emotion count for the years 2021 and 2022 combined
total_emotion_count <- sum(monthly_emotion_count$Total_Emotion_Count)

# Add a percentage column with one decimal place
monthly_emotion_count <- monthly_emotion_count %>%
  mutate(Percentage = round((Total_Emotion_Count / total_emotion_count) * 100, 1))

# Print the percentage of total emotions per month for 2021-2022
print(monthly_emotion_count)
```

```{r}
# Kalkulasi tahun 2021 sampai dengan tahun 2022

# Load the necessary library
library(tidyverse)

# Read the dataset
df_count <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')

# Convert date column to Date type if it's not already
df_count <- df_count %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"))  # replace `date_column` with actual date column name

# Filter for the years 2021 and 2022, exclude 'Ambiguous' category, then group by emotion
annual_emotion_count <- df_count %>%
  filter(format(date, "%Y") %in% c("2021", "2022"), emotion != "ambiguous") %>%
  group_by(emotion) %>%
  summarise(Emotion_Count = n(), .groups = "drop")

# Calculate the total count of all emotions for the years 2021 and 2022 combined
total_emotions <- sum(annual_emotion_count$Emotion_Count)

# Add a percentage column for each emotion based on the combined total
annual_emotion_count <- annual_emotion_count %>%
  mutate(Percentage = round((Emotion_Count / total_emotions) * 100, 1))

# Print the result
print(annual_emotion_count)
```







### BISA DILAKUKAN ####

```{r}
silentinvasionv4_2021_2022_with_emotions_v14 <- read.csv('silentinvasionv4_2021_2022_with_emotions_v14.csv')
```

```{r}
# Load the necessary libraries
library(udpipe)

# Download Turkish language model
udpipe_download_model(language = "turkish")
```

```{r}
# FIRST CLEANING
library(tm)

# Create a new dataframe
df_predicted_removeduplicates <- df_predicted

# Remove duplicate rows based on the text column, keeping the first occurrence
df_predicted_removeduplicates <- df_predicted_removeduplicates %>% distinct(text, .keep_all = TRUE)

# Remove whitespace
df_predicted_removeduplicates$text <- stripWhitespace(df_predicted_removeduplicates$text)
```


```{r}
# UPDATE CODE 1
# Load the necessary libraries
#library(udpipe)
#library(dplyr)
#library(stringr)

# Create a new dataframe for removing dots and other processing
#df_predicted_lemmatized <- df_predicted_removedots

# Load the Turkish language model
#turkish_model <- udpipe_load_model("turkish-imst-ud-2.5-191206.udpipe")

# Create a function to lemmatize words
#lemmatize_turkish <- function(text, model) {
#  annotations <- udpipe_annotate(model, x = text)
#  lemmatized_text <- as.data.frame(annotations)
#  return(paste(lemmatized_text$lemma, collapse = " "))
#}

# Lemmatize the words in the text column
#df_predicted_lemmatized$text <- sapply(df_predicted_lemmatized$text, function(x) {
#  x <- lemmatize_turkish(x, turkish_model)
#  return(x)
#})

# Remove whitespace
#df_predicted_lemmatized$text <- stripWhitespace(df_predicted_lemmatized$text)

# Delete the leading and trailing spaces
#df_predicted_lemmatized$text <- trimws(df_predicted_lemmatized$text)

```

```{r}
library(tm)
library(dplyr)
library(stringr)

# Remove stopwords
turkishstopwords <- readLines("TurkishSentiment-Stopwords.txt")
df_predicted_removeduplicates$text <- removeWords(df_predicted_removeduplicates$text, turkishstopwords)

# Function to remove punctuations at the beginning and end of each word
# and punctuations that are preceded and followed by whitespace
remove_edge_punctuations <- function(text) {
  # Remove punctuations preceded and followed by whitespace
  text <- gsub("\\s+[[:punct:]]+\\s+", " ", text)
  # Remove punctuations at the beginning of each word
  text <- gsub("\\b[[:punct:]]+", "", text)
  # Remove punctuations at the end of each word
  text <- gsub("[[:punct:]]+\\b", "", text)
  # Additional step: Remove punctuations directly next to a word
  text <- gsub("\\s+[[:punct:]]+", " ", text)
  text <- gsub("[[:punct:]]+\\s+", " ", text)
  # Remove "NA" and numbers
  text <- gsub("\\bNA\\b", "", text)
  text <- gsub("\\b\\d+\\b", "", text)
  return(text)
}

# Apply the function to the text column
df_predicted_removeduplicates$text <- sapply(df_predicted_removeduplicates$text, remove_edge_punctuations)

# Remove whitespace
df_predicted_removeduplicates$text <- stripWhitespace(df_predicted_removeduplicates$text)

# Delete the leading and trailing spaces
df_predicted_removeduplicates$text <- trimws(df_predicted_removeduplicates$text)
```


```{r}
# write dftweets dataframe into silentinvation-prediction.csv file
#write.csv(silentinvasiontest2022, "silentinvasiontest2022NOSTPWRD-v2.csv", row.names = FALSE)
```


```{r}
# Isolate text from tweets: tweets_text
df_predicted_removeduplicates_text <- df_predicted_removeduplicates$text

# Create a data frame with the text column
df_predicted_removeduplicates_text <- data.frame(text = df_predicted_removeduplicates_text)

# write dftweets dataframe into silentinvation-prediction.csv file
write.csv(df_predicted_removeduplicates_text, "df_predicted_removeduplicates_text-v1.csv", row.names = FALSE)

```


```{r}
# Read csv file
#silentinvasiontest2022 <- read.csv("silentinvasiontest2022_textNOSTPWRD-v2.csv")
```

## Most frequent words

```{r}
# Use the table() function to count the frequency of each word
word_counts <- table(unlist(strsplit(df_predicted_removeduplicates$text, " ")))
```


```{r}
# Use the sort() function to sort the word counts in descending order
sorted_word_counts <- sort(word_counts, decreasing = TRUE)

# Print the most frequent words
sorted_word_counts[1:30]
```


```{r}
library(wordcloud)

# Create a word cloud object
wordcloud(words = names(sorted_word_counts), freq = sorted_word_counts, scale=c(2.5,.5), min.freq = 1, max.words = 30, colors = brewer.pal(8, "Dark2"))

```

```{r}
library(wordcloud)
library(RColorBrewer)

# Exclude specific words
words_to_exclude <- c("kullanıcı", "bağlantı", "adresi", "retweetlemek", "sessiz", "istila", "sessizistila", "istilâ")
filtered_word_counts <- sorted_word_counts[!names(sorted_word_counts) %in% words_to_exclude]

# Create a word cloud object displaying the filtered words
wordcloud(words = names(filtered_word_counts), freq = filtered_word_counts, scale = c(2.5, 0.5), 
          min.freq = 80, max.words = 60, colors = brewer.pal(8, "Dark2"))
```

From this worldcloud, The most important messeges is:
türk = as a nationalism 
mülteci = as a refugees 
suriyeli = as a origin of the refugees 
işgal = as a job 
afgan = as a origin of the refugees  

```{r}
# Use the sort() function to sort the word counts in descending order
sorted_word_counts <- sort(filtered_word_counts, decreasing = TRUE)

# Print the most frequent words
sorted_word_counts[1:30]
```

```{r}
# filename: generate_wordclouds_by_emotion.R
# Purpose: Generate word clouds for each emotion in the dataframe

# Load necessary libraries
library(dplyr)
library(wordcloud)
library(RColorBrewer)

# Function to create word cloud for each emotion
create_wordcloud <- function(df, emotion) {
  # Filter the dataframe for the specific emotion
  emotion_df <- df %>% filter(emotion == !!emotion)
  
  # Count word frequencies
  word_counts <- table(unlist(strsplit(emotion_df$text, " ")))
  
  # Sort word counts in descending order
  sorted_word_counts <- sort(word_counts, decreasing = TRUE)
  
  # Exclude specific words
  words_to_exclude <- c("kullanıcı", "bağlantı", "adresi", "retweetlemek", "sessiz", "istila", "sessizistila", "istilâ")
  filtered_word_counts <- sorted_word_counts[!names(sorted_word_counts) %in% words_to_exclude]
  
  # Create and display the word cloud
  wordcloud(words = names(filtered_word_counts), freq = filtered_word_counts, scale = c(2.5, 0.5), 
            min.freq = 60, max.words = 60, colors = brewer.pal(8, "Dark2"))
  
  # Add a title to the plot
  title(main = paste("Word Cloud for Emotion:", emotion))
}

# Unique emotions in the dataframe excluding 'ambiguous'
emotions <- unique(df_predicted_removeduplicates$emotion)
emotions <- emotions[emotions != "ambiguous"]

# Create word clouds for each emotion
par(mfrow = c(2, 3))  # Adjust the layout to fit multiple plots
for (emotion in emotions) {
  create_wordcloud(df_predicted_removeduplicates, emotion)
}
```

```{r}
# filename: top_words_by_emotion.R
# Purpose: Display the 10 most frequent words in descending order for each emotion

# Load necessary libraries
library(dplyr)

# Function to get top 10 words for each emotion
get_top_words <- function(df, emotion) {
  # Filter the dataframe for the specific emotion
  emotion_df <- df %>% filter(emotion == !!emotion)
  
  # Count word frequencies
  word_counts <- table(unlist(strsplit(emotion_df$text, " ")))
  
  # Sort word counts in descending order
  sorted_word_counts <- sort(word_counts, decreasing = TRUE)
  
  # Exclude specific words
  words_to_exclude <- c("kullanıcı", "bağlantı", "adresi", "retweetlemek", "sessiz", "istila", "sessizistila", "istilâ", "kısa", "bi")
  filtered_word_counts <- sorted_word_counts[!names(sorted_word_counts) %in% words_to_exclude]
  
  # Get top 10 words
  top_words <- head(filtered_word_counts, 10)
  
  return(top_words)
}

# Unique emotions in the dataframe excluding 'ambiguous'
emotions <- unique(df_predicted_removeduplicates$emotion)
emotions <- emotions[emotions != "ambiguous"]

# Display top 10 words for each emotion
for (emotion in emotions) {
  cat("Top 10 words for emotion:", emotion, "\n")
  print(get_top_words(df_predicted_removeduplicates, emotion))
  cat("\n")
}

```

#From the sadness emotion, the important words are:
mülteci = related to refugee      
Türk = related to nation, patriotism
ülke = related to nation, patriotism 
#Turkiye's situation regarding refugees

#From the surprise emotion, the important words are:
gümbür = exploded
Türk = related to country
filmi = film
#Sessiz Istila's short film exploded in Turkiye

#From the fear emotion, the important words are:
hande = related to the name of the film producer
karacasu = related to the name of the film producer
gözaltına = related to punished, 
#Short film maker Sessiz Istila sentenced

#From the anger emotion, the important words are:
Türk = related to nation, patriotism
mülteci = related to refugees
işgal = related to jobs
#Turkiye has problems with refugess and employment

#From the happy emotion, the important words are:
güzel = related to excelent
hande = related to the name of the film producer
filmi = film
#Appreciation to the producer who made the short film Sessix Istilla

#From the disgust emotion, the important words are:


```{r}
# Bigram
# Load the tidytext package
library(dplyr)
library(tidytext)

# Create a data frame with one row for each bigram and one column for each word
bigrams <- df_predicted_removeduplicates %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

# Count the number of occurrences of each bigram
bigram_counts <- bigrams %>%
  count(bigram, sort = TRUE)
```


```{r}
# Head
bigram_counts$bigram[1:40]
```


From bigram analysis. The concern of the narative is in economic sector. On trigram, they add security issue, immigrants tried to rob the villages.

```{r}
# filename: count_bigrams_by_emotion.R
# Purpose: Count bigrams for each emotion in the dataframe

# Load necessary libraries
library(dplyr)
library(tidytext)

# Function to count bigrams for each emotion
count_bigrams <- function(df, emotion) {
  # Filter the dataframe for the specific emotion
  emotion_df <- df %>% filter(emotion == !!emotion)
  
  # Create bigrams
  bigrams <- emotion_df %>%
    unnest_tokens(bigram, text, token = "ngrams", n = 2)
  
  # Count the number of occurrences of each bigram
  bigram_counts <- bigrams %>%
    count(bigram, sort = TRUE)
  
  # Exclude specific words
  words_to_exclude <- c("kullanıcı", "bağlantı", "adresi", "retweetlemek", "sessiz", "istila", "sessizistila", "istilâ")
  bigrams_to_exclude <- outer(words_to_exclude, words_to_exclude, paste)
  bigrams_to_exclude <- as.vector(bigrams_to_exclude)
  
  # Filter out excluded bigrams
  filtered_bigram_counts <- bigram_counts %>%
    filter(!bigram %in% bigrams_to_exclude)
  
  return(filtered_bigram_counts)
}

# Unique emotions in the dataframe excluding 'ambiguous'
emotions <- unique(df_predicted_removeduplicates$emotion)
emotions <- emotions[emotions != "ambiguous"]

# Count bigrams for each emotion and print the top 40 bigrams
for (emotion in emotions) {
  cat("\nTop Bigrams for Emotion:", emotion, "\n")
  bigram_counts <- count_bigrams(df_predicted_removeduplicates, emotion)
  print(bigram_counts$bigram[1:10])
}
```

#From the sadness emotion, the important words are:
istila memleketimizde = related to invasion in our country    
memleketimizde mülteci = related to refugee in our country
#Turkiye's situation regarding refugees

#From the surprise emotion, the important words are:
istila filmi = invasion movie
#Sessiz Istila's short film/ Invasion movie

#From the fear emotion, the important words are:
karacasu gözaltına = related to karacasu detained
#Short film maker Sessiz Istila detained

#From the anger emotion, the important words are:
bot hesap = related to bot account
fetö yanlısı = related to FETO organisation
pkk yanlısı = related to PKK organisation
#The three bigrams has a same weight

#From the happy emotion, the important words are:
güzel = related to excelent
hande = related to the name of the film producer
filmi = film
#Appreciation to the producer who made the short film Sessix Istilla

```{r}
# Trigram
# Load the tidytext package
library(dplyr)
library(tidytext)

# Create a data frame with one row for each trigram and one column for each word
trigram <- df_predicted_removeduplicates %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)

# Count the number of occurrences of each trigram
trigram_counts <- trigram %>%
  count(trigram, sort = TRUE)
```


```{r}
# Head
trigram_counts$trigram[1:40]
```


```{r}
# 4-gram
# Load the tidytext package
library(dplyr)
library(tidytext)

# Create a data frame with one row for each bigram and one column for each word
fourgram <- df_predicted_removeduplicates %>%
  unnest_tokens(fourgram, text, token = "ngrams", n = 4)

# Count the number of occurrences of each bigram
fourgram_counts <- fourgram %>%
  count(fourgram, sort = TRUE)
```


```{r}
# Head
fourgram_counts$fourgram[1:40]
```


























### JANGAN DILAKUKAN DULU ####
### JANGAN DILAKUKAN DULU ####
### JANGAN DILAKUKAN DULU ####

## Calculate TF-IDF 

```{r}
# Load necessary libraries
library(tidytext)
library(dplyr)

# Tokenize the text data
tokens <- df_predicted_lemmatized %>%
  mutate(doc_id = row_number()) %>%
  unnest_tokens(word, text)

# Calculate term frequency (TF)
term_frequency <- tokens %>%
  count(doc_id, word, sort = TRUE)

# Calculate document frequency (DF)
doc_frequency <- term_frequency %>%
  group_by(word) %>%
  summarise(docs = n_distinct(doc_id))

# Calculate inverse document frequency (IDF)
inverse_doc_frequency <- doc_frequency %>%
  mutate(idf = log(nrow(term_frequency) / docs))

# Calculate TF-IDF
tf_idf <- term_frequency %>%
  left_join(inverse_doc_frequency, by = "word") %>%
  mutate(tf_idf = n * idf)

# View the results
head(tf_idf)

```


```{r}
# Load necessary library
library(ggplot2)

# Set the number of top words to visualize
top_n <- 30

# Calculate average TF-IDF scores for each word
average_tf_idf <- tf_idf %>%
  group_by(word) %>%
  summarize(avg_tf_idf = mean(tf_idf)) %>%
  arrange(desc(avg_tf_idf))

# Select the top N words with the highest average TF-IDF scores
top_words <- head(average_tf_idf, top_n)

# Create a bar plot
ggplot(top_words, aes(x = reorder(word, -avg_tf_idf), y = avg_tf_idf)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Top words by average TF-IDF",
       x = "Word",
       y = "Average TF-IDF") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


```{r}
# View the structure of tweets
str(df_predicted_lemmatized)
```


```{r}
# Print out the number of rows in tweets
nrow(df_predicted_lemmatized)
```


```{r}
# Isolate text from tweets: tweets_text
df_predicted_lemmatized_text <- df_predicted_lemmatized$text
str(df_predicted_lemmatized_text)
```


```{r}
library(tm)
df_predicted_lemmatized_source <- VectorSource(df_predicted_lemmatized_text)
```


```{r}
# Make a volatile corpus: tweets_corpus
df_predicted_lemmatized_corpus <- VCorpus(df_predicted_lemmatized_source)

# Print out the tweets_corpus
df_predicted_lemmatized_corpus
```


```{r}
# Print data on the 15th tweet in tweets_corpus
df_predicted_lemmatized_corpus[[15]]
```


```{r}
# Print the content of the 15th tweet in tweets_corpus
df_predicted_lemmatized_corpus[[15]][1]
```


```{r}
str(df_predicted_lemmatized_corpus[[15]])
```


```{r}
# Convert to corpus.prep
corpus.prep <- df_predicted_lemmatized_corpus
```


```{r}
## the output is truncated here to save space
content(corpus.prep[[1501]]) # Essay No. 1501
```


```{r}
### Section 5.1.2: Document-Term Matrix

dtm <- DocumentTermMatrix(corpus.prep)
dtm
```


```{r}
inspect(dtm[1:5, 1:8])
```


```{r}
dtm.mat <- as.matrix(dtm)
```


```{r}
library(wordcloud)
```


```{r}
wordcloud(colnames(dtm.mat), dtm.mat[12, ], max.words = 20, scale=c(2.5,.5), min.freq = 40, colors = brewer.pal(8, "Dark2"))  # essay No. 12
wordcloud(colnames(dtm.mat), dtm.mat[24, ], max.words = 20, scale=c(1.5,.5), min.freq = 40, colors = brewer.pal(8, "Dark2"))  # essay No. 24
wordcloud(colnames(dtm.mat), dtm.mat[1497, ], max.words = 20, scale=c(1.5,.5), min.freq = 40, colors = brewer.pal(8, "Dark2"))  # essay No. 24
```


```{r}
dtm.tfidf <- weightTfIdf(dtm) # tf-idf calculation
```


```{r}
dtm.tfidf.mat <- as.matrix(dtm.tfidf)  # convert to matrix
```


```{r}
## 10 most important words for Paper No. 12
head(sort(dtm.tfidf.mat[12, ], decreasing = TRUE), n = 10)

## 10 most important words for Paper No. 24
head(sort(dtm.tfidf.mat[24, ], decreasing = TRUE), n = 10)

## 10 most important words for Paper No. 1497
head(sort(dtm.tfidf.mat[1497, ], decreasing = TRUE), n = 10)
```


```{r}
k <- 10  # number of clusters
## subset The Federalist papers written by Hamilton
#hamilton <- c(1, 6:9, 11:13, 15:17, 21:36, 59:61, 65:85)
#dtm.tfidf.hamilton <- dtm.tfidf.mat[hamilton, ]
hamilton <- c(6:18, 33:181, 1073:1496, 1497:1502)
dtm.tfidf.hamilton <- dtm.tfidf.mat[hamilton, ]
```


```{r}
# Check dimensions of dtm.tfidf.mat
dim(dtm.tfidf.mat)
```


```{r}
## run k-means
km.out <- kmeans(dtm.tfidf.hamilton, centers = k)
km.out$iter # check the convergence; number of iterations may vary

## label each centroid with the corresponding term
colnames(km.out$centers) <- colnames(dtm.tfidf.hamilton)

for (i in 1:k) { # loop for each cluster
    cat("CLUSTER", i, "\n")
    cat("Top 10 words:\n") # 10 most important terms at the centroid
    print(head(sort(km.out$centers[i, ], decreasing = TRUE), n = 10))
    cat("\n")
    cat("Federalist Papers classified: \n") # extract essays classified
    cat(rownames(dtm.tfidf.hamilton)[km.out$cluster == i])
    cat("\n")
    cat("\n")
}
```

### JANGAN DILAKUKAN DULU ####
### JANGAN DILAKUKAN DULU ####
### JANGAN DILAKUKAN DULU ####
### JANGAN DILAKUKAN DULU ####






## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
