---
title: "sessiz istila"
author: "Darmawan Wicaksono"
date: "2022-12-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

From: https://www.frontiersin.org/articles/10.3389/fpsyg.2019.00781/full
Ekman proposed seven basic emotions: fear, anger, joy, sad, contempt, disgust, and surprise; but he changed to six basic emotions: fear, anger, joy, sadness, disgust, and surprise. However, a recent study found that disgust and anger shared similar wrinkled nose, and fear and surprise shared raised eyebrows (Jack et al., 2014). The differences between anger and disgust and the differences between fear and surprise, are thought to have developed later for social functions and not for survival per se (Mansourian et al., 2016). As such, Jack et al. (2014) proposed that we humans have four basic emotions: fear, anger, joy, and sad.

Conclusion: 
Four basic emotions: fear, anger, joy, and sad

## R Markdown

## Get all tweets from 2021 to 2022, from first time "sessiz istila" found on twitter until Dec 2022. Data taken at Jan 26, 2022

```{r}
library(academictwitteR)
silentinvasiontweet = get_all_tweets(
  query = "sessiz istila",
  exact_phrase = T,
    start_tweets = "2021-06-01T00:00:00Z",
    end_tweets = "2022-12-31T00:00:00Z",
    lang = "tr",
    file = "silentinvasiontweetfirst",
    data_path = "/Users/darmawan/Documents/rstudio/silentinvasion/json2",
    n=Inf
  )
```

```{r}
library(writexl)
tweets <- bind_tweets(data_path = "/Users/darmawan/Documents/rstudio/silentinvasion/json2")
write_xlsx(tweets, "/Users/darmawan/Documents/rstudio/silentinvasion/json2/silentinvasiontweethistory.xlsx")
```

```{r}
# Saving data frame:
save(silentinvasiontweet, file = "silentinvasiontweethistory.RData")
```

```{r}
# Load Rdata:
load("silentinvasiontweethistory.RData")
```

```{r}
# Saving text tweet into new dataframe
tweettext <- subset(silentinvasiontweet, select=c("id", "text"))
```


```{r}
# Saving data frame to *.csv file:
write.csv(tweettext, file = "tweettext.csv", row.names = FALSE)
```


```{r}
# Subset date and tweets text
silentinvasiontest <- subset(silentinvasiontweet, select = c("created_at","text"))
```


```{r}
# Saving data frame to *.csv file:
write.csv(silentinvasiontest, file = "silentinvasiontest.csv", row.names = FALSE)
```


```{r}
library(dplyr)
silentinvasiontest %>%
  filter(date == "2021-06-08")
```

First tweet who contained "sessiz istila" keyword are @KaracasuHande tweet (https://twitter.com/KaracasuHande/status/1402203834668273665) in June 8, 2021, she's quoted a tweet from @Haberinizcomtr (https://twitter.com/Haberinizcomtr/status/1402203342445613063) account, who also quote a web link from Haberiniz news site (https://haberiniz.com.tr/turk-milliyetciligi/adana-ayyildiz-hareketi-lideri-umit-ozdaga-suriyelilerden-dert-yandi-08062021). @KaracasuHande tweet retweeted by 3 account at that date. 


## Subsetting get_all_tweet dataframe

```{r}
silentinvasiontest <- read.csv("silentinvasiontest.csv")
```


```{r}
# Load the utils package
library(utils)

# Convert the date column to the ISO 8601 format
silentinvasiontest$date <- strptime(silentinvasiontest$created_at, format = "%Y-%m-%dT%H:%M:%S.%OSZ")

# Extract the days from each date
silentinvasiontest$date <- format(silentinvasiontest$date, "%Y-%m-%d")
```


```{r}
library(dplyr)

#group the data by date and count the number of tweets per date
datasilentinvasiontest <- silentinvasiontest %>% group_by(date) %>% summarize(tweet_count = n())
```


```{r}
# Create year column
library(lubridate)

datasilentinvasiontest$year <- year(datasilentinvasiontest$date)
```


```{r}
# Create month collumn
library(lubridate)

datasilentinvasiontest$month <- month(datasilentinvasiontest$date)
```



```{r}
# Saving data frame:
save(datasilentinvasiontest, file = "silentinvasion.RData")

# Saving data frame to *.csv file:
write.csv(datasilentinvasiontest, file = "silentinvasion.csv", row.names = FALSE)

```



## Calculate tweet count data

```{r}
# Read *.csv file:
silentinvasion <- read.csv("silentinvasion.csv")
```

```{r}
sum(silentinvasion$tweet_count)
```

From Twitter historical data using keyword "sessiz istila" from June 1, 2021 to December 30, 2022. We got 47,024 tweets. 


```{r}
# Sum tweet count for 2021
year_2021_tweet_count = sum(silentinvasion$tweet_count[(as.Date(silentinvasion$date, "%Y-%m-%d") >= as.Date("2021-01-01")) & (as.Date(silentinvasion$date, "%Y-%m-%d") <= as.Date("2021-12-31"))])

# Sum tweet count for 2022
year_2022_tweet_count = sum(silentinvasion$tweet_count[(as.Date(silentinvasion$date, "%Y-%m-%d") >= as.Date("2022-01-01")) & (as.Date(silentinvasion$date, "%Y-%m-%d") <= as.Date("2022-12-31"))])

```


```{r}
sum(year_2021_tweet_count)
```

In 2021 it self, from June 1, 2021 to December 30, 2021, we got 1,502 tweets.


```{r}
sum(year_2022_tweet_count)
```

In 2022 it self, from January 1, 2022 to December 30, 2022, we got 45,522 tweets. A sighnificant increased, more than 30 times since 2021. 


```{r}
# Load the utils package
#library(utils)

# Convert the date column to the ISO 8601 format
#silentinvasion$date <- strptime(silentinvasion$start, format = "%Y-%m-%dT%H:%M:%S.%OSZ")
```

```{r}
# Extract the days from each date
#silentinvasion$days <- format(silentinvasion$date, "%Y-%m-%d")
```


```{r}
# Extract the year from each date
#library(lubridate)
#silentinvasion$year <- year(silentinvasion$date)
```


```{r}
# Check class column
class(silentinvasion$tweet_count)
class(silentinvasion$date)
class(silentinvasion$month)
class(silentinvasion$year)
```

```{r}
# delete empty row from dataframe
#silentinvasion <- na.omit(silentinvasion)
```

```{r}
# Change tweet_count into numeric
silentinvasion$tweet_count <- as.numeric(silentinvasion$tweet_count)

# Change days into date format
silentinvasion$date <- as.Date(silentinvasion$date,format="%Y-%m-%d")

# Change month into numeric
silentinvasion$month <- as.numeric(silentinvasion$month)

# Change year into numeric
silentinvasion$year <- as.numeric(silentinvasion$year)

```


```{r}
# Check class column
class(silentinvasion$tweet_count)
class(silentinvasion$date)
class(silentinvasion$month)
class(silentinvasion$year)
```


```{r}
# Summary of data
summary(silentinvasion$tweet_count)
```


```{r}
# Sum the numeric data by Date
summed_data <- aggregate(silentinvasion$tweet_count, by = list(Date = silentinvasion$date), sum)
```


```{r}
# Summary of data, per year
summary(summed_data)
```

Tweets data from 2021 to 2022, we got the least tweet per day using "sessiz istila" keyword is 1, and the maximum tweets using it is 6,077. Mean is 133.2 and median 13. For the first quartile is 3, and third quartile is 35 tweets.  


```{r}
library(dplyr)
silentinvasion %>%
  filter(tweet_count == "1")
```

There was 51 days has a single tweet contain "sessiz istila" keyword.


```{r}
library(dplyr)
silentinvasion %>%
  filter(tweet_count == "6077")
```

Highest number of tweet in June 27, 2022, as much as 6,077 tweets in one day. The highest number since 2021 until 2022. 


```{r}
# Calculate 1st Qu. and 3rd Qu.
q1 <- quantile(summed_data$x, probs = 0.25)
q3 <- quantile(summed_data$x, probs = 0.75)
```


```{r}
# Make overall graph from 2021 to 2022
# First, load the ggplot2 library
library(ggplot2)
library(scales)

# Next, create a data frame with the tweet_count and date data
df <- data.frame(silentinvasion$tweet_count, silentinvasion$date)

# find the position of the highest value
max_pos <- which.max(silentinvasion$tweet_count)

# create the label for the text annotation
label_text <- paste("  Highest tweet on:", silentinvasion$date[max_pos], "as much as:",  silentinvasion$tweet_count[max_pos], "tweets")

# Then, use ggplot2 to create a line graph with tweet_count on the y-axis and date on the x-axis
ggplot(data = df, aes(x = silentinvasion$date, y = silentinvasion$tweet_count)) + 
  geom_line() +
  ggtitle("Tweet Count from Jun 2021 - Dec 2022") +
  xlab("Month") +
  ylab("Tweet Count") +
  geom_text(aes(x = silentinvasion$date[max_pos], y = silentinvasion$tweet_count[max_pos]),
            label = label_text, hjust=1.02, col = "blue") +
scale_x_date(breaks = "1 month", labels = date_format("%b"), minor_breaks = "1 month") +
  geom_hline(yintercept = q1, color = "blue") +
  geom_hline(yintercept = q3, color = "red")

```



## Split the years, 2021 and 2022
## Year 2021

```{r}
year_2021_data <- subset(silentinvasion, year == 2021)
year_2022_data <- subset(silentinvasion, year == 2022)
```


```{r}
# Sum tweet count for 2021
year_2021_summed_data <- aggregate(year_2021_data$tweet_count, by = list(Date = year_2021_data$date), sum)

# Sum tweet count for 2022
year_2022_summed_data <- aggregate(year_2022_data$tweet_count, by = list(Date = year_2022_data$date), sum)
```


```{r}
# Summary of 2021 data
summary(year_2021_summed_data)
```

Tweets data from 2021, we got the least tweet per day using "sessiz istila" keyword is 1, and the maximum tweets using it is 648. Mean is 25.03 and median 2. For the first quartile is 1, and third quartile is 4.25 tweets. Relatively low tweets using "sessiz istila" keyword. We can say that issue not really popular.


```{r}
library(dplyr)
year_2021_data %>%
  filter(tweet_count == "1")
```

There was 26 days has a single tweet contain "sessiz istila" keyword.


```{r}
library(dplyr)
year_2021_data %>%
  filter(tweet_count == "648")
```

Highest number of tweet in July 19, 2021, as much as 648 tweets in one day. The highest number in 2021. 


```{r}
# Calculate mean 2021
mean_2021 <- mean(year_2021_summed_data$x)
```


```{r}
# Graph year 2021
# First, load the ggplot2 library
library(ggplot2)
library(scales)

# Next, create a data frame with the tweet_count and date data
df <- data.frame(year_2021_data$tweet_count, year_2021_data$date)

# find the position of the highest value
max_pos <- which.max(year_2021_data$tweet_count)

# create the label for the text annotation
label_text <- paste("  Highest tweet on:", year_2021_data$date[max_pos], "as much as:",  year_2021_data$tweet_count[max_pos], "tweets")

# Then, use ggplot2 to create a line graph with tweet_count on the y-axis and date on the x-axis
ggplot(data = df, aes(x = year_2021_data$date, y = year_2021_data$tweet_count)) + 
  geom_line() +
  ggtitle("Tweet Count over Time") +
  xlab("Month, 2021") +
  ylab("Tweet Count") +
  geom_text(aes(x = year_2021_data$date[max_pos], y = year_2021_data$tweet_count[max_pos]),
            label = label_text, hjust=0, col = "blue") +
scale_x_date(breaks = "1 month", labels = date_format("%b"), minor_breaks = "1 week") +
  geom_hline(yintercept = mean_2021, color = "red")

```

In 2021, it has 2 peaks of the amount of tweets. First one in 3rd week of July, and 2st week of December.


## Year 2021, July
```{r}
# Tweets on the exact date
library(dplyr)
silentinvasiontest %>%
  filter(date == "2021-07-17")
```

Second pikes of the tweet who contained "sessiz istila" keyword in July 17, 2021. When @aykiricomtr account (https://twitter.com/aykiricomtr/status/1416335549149888515) posted a tweet contain a web link from Aykiri news site (https://www.aykiri.com.tr/sessiz-istila-devam-ediyor-turkiye-ye-giren-kacaklar-tir-kasasinda-nigde-ye-geldi/12969/). @aykiricomtr tweet itself retweeted by 327 account. 


```{r}
# Tweets on the exact date
library(dplyr)
silentinvasiontest %>%
  filter(date == "2021-07-19")
```

Peak of the tweet who contained "sessiz istila" keyword in July 19, when @aykiricomtr account (https://twitter.com/aykiricomtr/status/1417070055062392832) posted a tweet contain a web link from Aykiri news site (https://www.aykiri.com.tr/sessiz-istila-devam-ediyor-van-sinirindan-kacak-yollarla-turkiye-ye-giren-binlerce-afgan-yine-goruntulendi/13008/). @aykiricomtr tweet itself retweeted by 638 account. 


```{r}
# Subset dataframe to July 2021
year_2021_july_data <- subset(silentinvasion, year == 2021 & month == 7)
```

```{r}
# Graph July 2021
# First, load the ggplot2 library
library(ggplot2)
library(scales)

# Next, create a data frame with the tweet_count and date data
dfmonth <- data.frame(year_2021_july_data$tweet_count, year_2021_july_data$date)

# find the position of the highest value
max_pos <- which.max(year_2021_july_data$tweet_count)

# create the label for the text annotation
label_text <- paste("  Highest tweet on:", year_2021_july_data$date[max_pos], "as much as:",  year_2021_july_data$tweet_count[max_pos], "tweets")

# Extract the day component from the dates and store it in a new variable
dfmonth$day <- as.integer(format(dfmonth$year_2021_july_data.date, "%d"))

# Then, use ggplot2 to create a line graph with tweet_count on the y-axis and date on the x-axis
ggplot(data = dfmonth, aes(x = year_2021_july_data$date, y = year_2021_july_data$tweet_count)) + 
  geom_line() +
  ggtitle("Tweet Count over Time") +
  xlab("July, 2021") +
  ylab("Tweet Count") +
  geom_text(aes(x = year_2021_july_data$date[max_pos], y = year_2021_july_data$tweet_count[max_pos]),
            label = label_text, hjust=0, col = "blue") +
  scale_x_date(date_labels = "%d", date_breaks = "1 day")

```


## Year 2021, December
```{r}
# Tweets on the exact date
library(dplyr)
silentinvasiontest %>%
  filter(date == "2021-12-03")
```

Peak of the tweet who contained "sessiz istila" keyword in December 3, when @batuhancolak33 account (https://twitter.com/batuhancolak33/status/1466775042822479880) posted a tweet quoted tweet of @aykiricomtr (https://twitter.com/aykiricomtr/status/1466768076741955585/). @batuhancolak33 tweet itself retweeted by 206 account. 


```{r}
# Subset dataframe to December 2021
year_2021_december_data <- subset(silentinvasion, year == 2021 & month == 12)
```

```{r}
# Graph December 2021
# First, load the ggplot2 library
library(ggplot2)
library(scales)

# Next, create a data frame with the tweet_count and date data
dfmonth <- data.frame(year_2021_december_data$tweet_count, year_2021_december_data$date)

# find the position of the highest value
max_pos <- which.max(year_2021_december_data$tweet_count)

# create the label for the text annotation
label_text <- paste("  Highest tweet on:", year_2021_december_data$date[max_pos], "as much as:",  year_2021_december_data$tweet_count[max_pos], "tweets")

# Extract the day component from the dates and store it in a new variable
dfmonth$day <- as.integer(format(dfmonth$year_2021_december_data.date, "%d"))

# Then, use ggplot2 to create a line graph with tweet_count on the y-axis and date on the x-axis
ggplot(data = dfmonth, aes(x = year_2021_december_data$date, y = year_2021_december_data$tweet_count)) + 
  geom_line() +
  ggtitle("Tweet Count over Time") +
  xlab("December, 2021") +
  ylab("Tweet Count") +
  geom_text(aes(x = year_2021_december_data$date[max_pos], y = year_2021_december_data$tweet_count[max_pos]),
            label = label_text, hjust=0, col = "blue") +
  scale_x_date(date_labels = "%d", date_breaks = "1 day")

```




## Year 2022

```{r}
# Summary of 2022 data
summary(year_2022_summed_data)

```

Tweets data from 2022, we got the least tweet per day using "sessiz istila" keyword is 1, and the maximum tweets using it is 6,077. Mean is 155.4 and median 18. For the first quartile is 6, and third quartile is 46 tweets. Jumped really high.


```{r}
library(dplyr)
year_2022_data %>%
  filter(tweet_count == "1")
```

There was 25 days has a single tweet contain "sessiz istila" keyword.


```{r}
library(dplyr)
year_2022_data %>%
  filter(tweet_count == "6077")
```

Highest number of tweet in Jule 27, 2022, as much as 6,077 tweets in one day. The highest number in 2022. 


```{r}
# Calculate mean 2021
mean_2022 <- mean(year_2022_summed_data$x)
```

```{r}
# Calculate 1st Qu. and 3rd Qu.
q1 <- quantile(year_2022_summed_data$x, probs = 0.25)
q3 <- quantile(year_2022_summed_data$x, probs = 0.75)
```

```{r}
# Graph year 2022
# First, load the ggplot2 library
library(ggplot2)
library(scales)

# Next, create a data frame with the tweet_count and date data
df <- data.frame(year_2022_data$tweet_count, year_2022_data$date)

# find the position of the highest value
max_pos <- which.max(year_2022_data$tweet_count)

# create the label for the text annotation
label_text <- paste("  Highest tweet on:", year_2022_data$date[max_pos], "as much as:",  year_2022_data$tweet_count[max_pos], "tweets")

# Then, use ggplot2 to create a line graph with tweet_count on the y-axis and date on the x-axis
ggplot(data = df, aes(x = year_2022_data$date, y = year_2022_data$tweet_count)) + 
  geom_line() +
  ggtitle("Tweet Count over Time") +
  xlab("Month, 2022") +
  ylab("Tweet Count") +
  geom_hline(yintercept = q1, color = "magenta") +
  geom_hline(yintercept = q3, color = "green") +
  geom_text(aes(x = year_2022_data$date[max_pos], y = year_2022_data$tweet_count[max_pos]),
            label = label_text, hjust=0, col = "blue") +
scale_x_date(breaks = "1 month", labels = date_format("%b"), minor_breaks = "1 week") +
  geom_hline(yintercept = mean_2022, color = "red")

```

In 2022, it has 3 big spikes. The biggest spike of the tweet that contained the "sessiz istila" keyword was on June 27, 2022, when @Yilmaz_Ozdill account (Özdil, 2022) quoted a tweet containing a tweet from @umitozdag account (Özdağ, 2022). @Yilmaz_Ozdill tweet itself was retweeted by 7699 accounts. The second spike of the tweet was on May 4, 2023, when @umitkocasakal_ account (Kocasakal, 2022) was retweeted by 1021 accounts.


```{r}
# Tweets on the exact date
library(dplyr)
silentinvasiontest %>%
  filter(date == "2022-06-27")
```


## Year 2022, June
```{r}
# Subset dataframe to June 2022
year_2022_june_data <- subset(silentinvasion, year == 2022 & month == 6)
```


```{r}
# Graph June 2022
# First, load the ggplot2 library
library(ggplot2)
library(scales)

# Next, create a data frame with the tweet_count and date data
dfmonth <- data.frame(year_2022_june_data$tweet_count, year_2022_june_data$date)

# find the position of the highest value
max_pos <- which.max(year_2022_june_data$tweet_count)

# create the label for the text annotation
label_text <- paste("  Highest tweet on:", year_2022_june_data$date[max_pos], "as much as:",  year_2022_june_data$tweet_count[max_pos], "tweets")

# Extract the day component from the dates and store it in a new variable
dfmonth$day <- as.integer(format(dfmonth$year_2022_june_data.date, "%d"))

# Then, use ggplot2 to create a line graph with tweet_count on the y-axis and date on the x-axis
ggplot(data = dfmonth, aes(x = year_2022_june_data$date, y = year_2022_june_data$tweet_count)) + 
  geom_line() +
  ggtitle("Tweet Count over Time") +
  xlab("June, 2022") +
  ylab("Tweet Count") +
  geom_text(aes(x = year_2022_june_data$date[max_pos], y = year_2022_june_data$tweet_count[max_pos]),
            label = label_text, hjust=1.01, col = "blue") +
  scale_x_date(date_labels = "%d", date_breaks = "1 day")

```


## Year 2022, May
```{r}
# Subset dataframe to May 2022
year_2022_may_data <- subset(silentinvasion, year == 2022 & month == 5)
```


```{r}
# Graph May 2022
# First, load the ggplot2 library
library(ggplot2)
library(scales)

# Next, create a data frame with the tweet_count and date data
dfmonth <- data.frame(year_2022_may_data$tweet_count, year_2022_may_data$date)

# find the position of the highest value
max_pos <- which.max(year_2022_may_data$tweet_count)

# create the label for the text annotation
label_text <- paste("  Highest tweet on:", year_2022_may_data$date[max_pos], "as much as:",  year_2022_may_data$tweet_count[max_pos], "tweets")

# Extract the day component from the dates and store it in a new variable
dfmonth$day <- as.integer(format(dfmonth$year_2022_may_data.date, "%d"))

# Then, use ggplot2 to create a line graph with tweet_count on the y-axis and date on the x-axis
ggplot(data = dfmonth, aes(x = year_2022_may_data$date, y = year_2022_may_data$tweet_count)) + 
  geom_line() +
  ggtitle("Tweet Count over Time") +
  xlab("May, 2022") +
  ylab("Tweet Count") +
  geom_text(aes(x = year_2022_may_data$date[max_pos], y = year_2022_may_data$tweet_count[max_pos]),
            label = label_text, hjust=0.01, col = "blue") +
  scale_x_date(date_labels = "%d", date_breaks = "1 day")

```

```{r}
# Tweets on the exact date
library(dplyr)
silentinvasiontest %>%
  filter(date == "2022-05-04")
```

```{r}
# Tweets on the exact date
library(dplyr)
silentinvasiontest %>%
  filter(date == "2022-05-10")
```

```{r}
library(dplyr)
silentinvasiontweet %>%
  filter(id == "1523876749427236864")
```




## From tweetext.csv, we copied tweets ID, and download all of the tweets data using NodeXL

```{r}
# Saving data frame:
save(tweettext, file = "tweettext.RData")

# Saving data frame into csv file:
write.csv(tweettext, "tweettext.csv", row.names = FALSE)
```


## From tweets data downloaded using NodeXL (excel format), load excel file into dataframe and subset only tweets text 

```{r}
# First, install and load the package
library(readxl)

# Then, use the read_excel() function to read the file
dftweets <- read_excel("silentinvasiontweethistory.xlsx")
```

```{r}
# subset dataframe silentinvasiontweethistory and write into silentinvasiontweethistory.csv
dftweetstext <- subset(dftweets, select = c("Entry", "OriginalEmotion", "ValidatedEmotion", "Condition", "VoteDistribution"))
```


## Build data for SNA and export it to gephi file

```{r}
# Load tweets 
tweets_bind_df <- bind_tweets(data_path = "/Users/darmawan/Documents/rstudio/silentinvasion/json2/") %>%  #for data stored in a data_path
  as_tibble()
tweets_bind_df_tidy <- bind_tweets(data_path = "/Users/darmawan/Documents/rstudio/silentinvasion/json2/", output_format = "tidy")
```

```{r}
# Unnest dataframe column entities
unnested_df <- unnest(tweets_bind_df, cols = entities, keep_empty = TRUE)
entities_df <- tweets_bind_df$entities %>%
  as_tibble()
```  

```{r}
# Extract mentions column as list
mentions_list <- entities_df$mentions
```  

```{r}
### If element in list is an empty list replace it with an empty dataframe
# Empty dataframe
empty_df <-
  data.frame(start = NA,
             end = NA,
             username = NA,
             id = NA)

# Loop
for (i in seq_along(mentions_list)) { # loop over elements in list
  if (!is.data.frame(mentions_list[[i]])) { # check if not a dataframe
    mentions_list[[i]] <- empty_df # replace with empty dataframe
  }
}
```  

```{r}
# Replace column with empty lists with column with empty dataframes
unnested_df$mentions <- mentions_list
``` 

```{r}
# Unnest mentions column to longer (i.e. one or more rows per tweet_id)
tweets_bind_df_longer <- unnest_longer(unnested_df, col = mentions)
``` 

```{r}
# Rename mentions columns and unnest mentions df
names(tweets_bind_df_longer$mentions)[names(tweets_bind_df_longer$mentions) == 'id'] <- 'mentions_id'
names(tweets_bind_df_longer$mentions)[names(tweets_bind_df_longer$mentions) == 'username'] <- 'mentions_username'

tweets_bind_df_mentions <- tweets_bind_df_longer %>% unnest(mentions)
```

```{r}
# Join by tweet_id
names(tweets_bind_df_mentions)[names(tweets_bind_df_mentions) == 'id'] <- 'tweet_id'
tweets_bind_df_mentions_narrow <- 
  tweets_bind_df_mentions[,c("tweet_id", "mentions_username", 
                                                  "mentions_id")]

tweets_bind_mentions_tidy_df <- 
  left_join(tweets_bind_df_tidy, tweets_bind_df_mentions_narrow, by='tweet_id') 
```


```{r}
# Saving data frame:
save(tweets_bind_mentions_tidy_df, file = "silentinvasionmentions.RData")
```


```{r}
# Saving data frame to *.csv file:
write.csv(tweets_bind_mentions_tidy_df, file = "silentinvasionmentions.csv", row.names = FALSE)
```

```{r}
library(igraph)
## Create graph
filter(tweets_bind_mentions_tidy_df, retweet_count > 0) %>%
  select(user_username, mentions_username) %>%
  unnest(mentions_username) %>% 
  filter(!is.na(mentions_username)) %>% 
  graph_from_data_frame() -> net

```

```{r}
summary(net)
```

```{r}
library(igraph)
write_graph(simplify(net),  "silentinvasionmentionsSNA.gml", format = "gml")
```



## Clean all tweet

```{r}
# Load Rdata:
load("tweettext.RData")
```

```{r}
# Make lower case
tweettext$text <- tolower(tweettext$text)
```

```{r}
library(stringr)

# Take out retweet header
tweettext$text <- str_replace(tweettext$text,"RT @[a-z,_,A-Z,0-9]*: ","")
tweettext$text <- str_replace(tweettext$text,"rt @[a-z,_,A-Z,0-9]*: ","")
tweettext$text <- str_replace(tweettext$text,"RT : ","")
tweettext$text <- str_replace(tweettext$text,"rt : ","")
```

```{r}
library(stringr)

# Get rid of references to other screennames
tweettext$text <- str_replace_all(tweettext$text,"@[a-z,_,A-Z,0-9]*","")
```

```{r}
library(stringr)

# Get rid of hashtags
tweettext$text <- str_replace_all(tweettext$text,"#[a-z,_,A-Z,0-9]*","")
```

```{r}
library(tm)
# Remove whitespace
tweettext$text <- stripWhitespace(tweettext$text)
```

```{r}
# Delete the leading and trailing spaces
tweettext$text <- trimws(tweettext$text)
```

```{r}
library(qdapRegex)

# Get rid of URLs
rm_twitter_n_url <- rm_(pattern=pastex("@rm_twitter_url", "@rm_url"))
tweettext$text <- rm_twitter_n_url(tweettext$text)

```


```{r}
# Remove all emoticons from the sentence
tweettext$text <- gsub("[^[:alnum:][:space:]]+", "", tweettext$text)
```


```{r}
# Remove numbers
tweettext$text <- removeNumbers(tweettext$text)
```


```{r}
# Remove whitespace
tweettext$text <- stripWhitespace(tweettext$text)
```

```{r}
# Delete the leading and trailing spaces
tweettext$text <- trimws(tweettext$text)
```

```{r}
# Subset data frame:
tweettext <- subset(tweettext, select="text")
```


```{r}
# Saving data frame into csv file:
write.csv(tweettext, "tweettextdataset.csv", row.names = FALSE)
```



## Stop in here to try machine learning

```{r}
tweettext <- read.csv("tweettextdataset.csv")
```


```{r}
# Remove stopwords
turkishstopwords <- readLines("TurkishSentiment-Stopwords.txt")
tweettext$text <- removeWords(tweettext$text, turkishstopwords)
```

```{r}
# Remove whitespace
tweettext$text <- stripWhitespace(tweettext$text)
```

```{r}
# Delete the leading and trailing spaces
tweettext$text <- trimws(tweettext$text)
```

```{r}
# Saving data frame into csv file:
write.csv(tweettext, "tweettextdatasetML.csv", row.names = FALSE)
```


## Stemming Turkish words but ignored for now, we try to use morphology method in python for better result

```{r}
# Load the SnowballC package
library(SnowballC)

# Define a function to stem the words in a sentence
stem_sentence <- function(sentence) {
  # Split the sentence into a list of words
  words <- strsplit(sentence, " ")[[1]]
  
  # Stem the words using the Turkish stemmer from SnowballC
  stemmed_words <- stemDocument(words, language = "turkish")
  
  # Join the stemmed words into a single string
  stemmed_sentence <- paste(stemmed_words, collapse = " ")
  
  return(stemmed_sentence)
}

# Use the apply function to apply the stem_sentence function to each row of the text column
tweettext$text <- apply(tweettext, 1, function(row) stem_sentence(row["text"]))
```


## Analysis all tweet

```{r}
tweettext <- read.csv("tweettextdatasetML.csv")
```


```{r}
# Use the table() function to count the frequency of each word
word_counts <- table(unlist(strsplit(tweettext$text, " ")))
```


```{r}
# Use the sort() function to sort the word counts in descending order
sorted_word_counts <- sort(word_counts, decreasing = TRUE)

# Print the most frequent words
sorted_word_counts[1:40]
```

From most frequent words in the tweets. We found 40's words as follows (in Turkish): 
istila, sessiz, işgal, kaçak, memleketin, serbest, suriyelilerin, kimliği, adresi, ikametgah, vilayetine, gidebilmesi, mill, partinin, stratejik, ensar, göç, evet, ülkemizi, ak (name of the Turkish party, AK Party), mühendisliği, örtülü, masalı, anlatarak, hande  (name of person), yüzde, karacasu  (name of person), el, gerçek, çataklı, sinsi, ığınmacısorunu, ılar, sarsıcı, gümbür, bot, yapan, içişleri, hesapların, altında 

If we translated in English as follows:
invasion, silent, occupation, fugitive, your hometown, free, syrians, identity, address, domicile, prefecture, ability to go, nationality, party, strategic, ensar, migration, yes, our country, ak (name of the Turkish party, AK Party), engineering, covered, tale, telling, hande  (name of person), percent, karacasu  (name of person), hand, real, fringed, sly, refugee problem, i will, jarring, rumble, bot (robot, as a twitter bots), making, interior, your accounts, under


```{r}
library(wordcloud)

# Create a word cloud object
wordcloud(words = names(sorted_word_counts), freq = sorted_word_counts, scale=c(2.5,.5), min.freq = 40, max.words = 300, colors = brewer.pal(8, "Dark2"))

```


```{r}
# Bigram
# Load the tidytext package
library(dplyr)
library(tidytext)

# Create a data frame with one row for each bigram and one column for each word
bigrams <- tweettext %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

# Count the number of occurrences of each bigram
bigram_counts <- bigrams %>%
  count(bigram, sort = TRUE)
```

```{r}
# Head
bigram_counts$bigram[1:40]
```

```{r}
# Trigram
# Load the tidytext package
library(dplyr)
library(tidytext)

# Create a data frame with one row for each trigram and one column for each word
trigram <- tweettext %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)

# Count the number of occurrences of each trigram
trigram_counts <- trigram %>%
  count(trigram, sort = TRUE)
```

```{r}
# Head
trigram_counts$trigram[1:40]
```

```{r}
# 4-gram
# Load the tidytext package
library(dplyr)
library(tidytext)

# Create a data frame with one row for each bigram and one column for each word
fourgram <- tweettext %>%
  unnest_tokens(fourgram, text, token = "ngrams", n = 4)

# Count the number of occurrences of each bigram
fourgram_counts <- fourgram %>%
  count(fourgram, sort = TRUE)
```

```{r}
# Head
fourgram_counts$fourgram[1:40]
```

```{r}
# Subset data frame:
bigramdata <- subset(bigram_counts, select="bigram")
```



## Making dataset for human coding

```{r}
tweettext <- read.csv("tweettextdataset.csv")
```


```{r}
# Cleaning duplicate row from trainingset data
tweettext <- unique(tweettext)
```


```{r}
# Remove whitespace
tweettext$text <- stripWhitespace(tweettext$text)
```


```{r}
# Delete the leading and trailing spaces
tweettext$text <- trimws(tweettext$text)
```


```{r}
# delete empty row from dataframe
tweettext <- na.omit(tweettext)
```


```{r}
# Saving data frame into csv file:
write.csv(tweettext, "tweettextdatasetclean.csv", row.names = FALSE)
```



## Using R, load trainingset.csv into trainingset dataframe. Then select 301 first rows on the dataframe, and save it as trainingsetabbas.csv

```{r}
# Load the csv file into a dataframe
trainingset <- read.csv("tweettextdatasetclean.csv")

# Select the first 301 rows of the dataframe
trainingsetabbas <- trainingset[1:400, ]

# Cleaning duplicate row from trainingset data
trainingsetabbas <- unique(trainingsetabbas)

# Delete the leading and trailing spaces
trainingsetabbas <- trimws(trainingsetabbas)

# Save the selected rows as a new csv file
write.csv(trainingsetabbas, "trainingsetabbas.csv", row.names = FALSE)
```


## First time "sessiz istila" found from journalist linked to Zafer Party. But isn't relatable because he talked about plants
```{r}
library(academictwitteR)
silentinvasion = count_all_tweets(
  query = "sessiz istila",
  exact_phrase = T,
    start_tweets = "2019-12-01T00:00:00Z",
    end_tweets = "2019-12-31T00:00:00Z",
    granularity = "day",
    n=Inf
  )
```


## We found starting issue "sessiz istila" from book published by Hande Karacasu posted on Twitter

```{r}
library(academictwitteR)
silentinvasion = count_all_tweets(
  query = "sessiz istila",
  exact_phrase = T,
    start_tweets = "2021-06-01T00:00:00Z",
    end_tweets = "2022-12-31T00:00:00Z",
    granularity = "day",
    n=Inf
  )
```

```{r}
sum(silentinvasion$tweet_count)
```


## Process tweet data



